### 2025-04-27 paper.tex
tracking paper

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{url}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tikz}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Formally Verifying Voter Security Properties in DAO Smart Contracts}

\author{
    \makebox[\textwidth][c]{%
        \begin{minipage}{0.45\textwidth}
            \centering
            \textbf{Anish Toomu} \\
            \textit{Department of Computer Science} \\
            \textit{University of North Carolina at Chapel Hill} \\
            Chapel Hill, North Carolina, USA
        \end{minipage}
        \hfill
        \begin{minipage}{0.45\textwidth}
            \centering
            \textbf{Aidan Maguire} \\
            \textit{Department of Computer Science} \\
            \textit{University of North Carolina at Chapel Hill} \\
            Chapel Hill, North Carolina, USA
        \end{minipage}
    }\\[1.5em]

    \makebox[\textwidth][c]{%
        \begin{minipage}{0.6\textwidth}
            \centering
            \textbf{Jeffrey Zhang} \\
            \textit{Department of Computer Science} \\
            \textit{University of North Carolina at Chapel Hill} \\
            Chapel Hill, North Carolina, USA
        \end{minipage}
    }
}

\maketitle

\section{Introduction}
This project aims to make use of two existing security tools to define and verify security properties for voting methods across a suite of Ethereum blockchain programs. Many Ethereum blockchain programs take the form of a DAO, or Decentralized Autonomous Organization, wherein users holding tokens that verify them as members of the organization can spend those tokens to vote on decision-making for the DAO as a whole. There are several types of vulnerabilities that have been identified in these types of contracts, but for this paper we will be looking at vulnerabilities surrounding the vote system that allow attackers to exploit the democratic principles behind DAOs.

Our proposal intends to formally verify a suite of the most used DAO contracts to confirm that they are secure. We will require the use of Scribble, a specification language that allows us to define security properties for DAO contracts as annotations within the contracts themselves. We will then use Mythril, a security-analysis tool, to verify each of our newly defined security properties for our suite of popular contracts. If successful, we will increase the confidence in these widely-used contracts. Possible challenges include the properties not being entirely specifiable in Scribble's specification language, and some contracts being too complex to analyze with Mythril due to state explosion.

\section{State of the Art}

DAOs are a type of smart contract that define the rules and structure of a organization. In more general terms, DAOs represent decentralized communities that can allocate resources without centralized leadership. While there exist tools for various methods of verifying and bug-finding in smart contracts including static analysis[1], model checking[2], and symbolic execution[3], they haven’t been narrowed down to focus on DAOs, and the specific exploits that come with their voting systems, a key, shared property across DAOs and a critical part of their operations. We have chosen to use an existing symbolic execution-based tool, Mythril[4], along with Scribble[5], a specification language for properties in this work.

\section{Background}
To understand our proposed enhancements to Mythril, we must first grasp the fundamental concepts of the blockchain, the Ethereum blockchain and its innovative smart contracts, and finally DAOs, a subset of smart contracts with common functionalities.

\subsection{Blockchain}
A blockchain serves as a ledger of transactions that is transparent, decentralized, and secure. Each block in the chain contains information about transactions allowing anyone to inspect them at any time. Additionally, each block contains a cryptographic hash of the previous block in the chain. This chain means that in the event of a block being tampered with by an attacker, all of the altered blocks' successors would also be changed. The consensus needed to accept a chain also provides further security. If the majority of the computational power on the network is controlled by honest parties then the honest chain will be accepted. An attacker seeking to change a block would need to alter the block, redo all the proof-of-work computation for it and its successor blocks, and then catch up to the honest chain to be accepted. This proves to be computationally infeasible[6].

\subsection{Ethereum and Smart Contracts}
Ethereum, as proposed by Vitalik Buterin in 2014, seeks to provide an alternative to Bitcoin with a focus on the development of decentralized applications. This is achieved through a blockchain that contains a built-in Turing-complete language[7]. This language allows users to write smart contracts that are stored on the blockchain. Smart contracts are a type of account, they have a balance and can be interacted with through transactions. They differ from users’ externally owned accounts in their method of control. Where externally owned accounts are controlled by user decisions, smart contracts are programs that run on the blockchain according to their code. Users or other smart contracts interact with smart contracts by sending a transaction that executes the functions defined by the contract’s code. Smart contracts automatically execute when their conditions are met, are universally visible, and are unable to be changed once uploaded[8]. In this way smart contracts provide a trustworthy, automated way to enforce agreements, reducing the need for third-party enforcement, minimizing exceptions, and lowering the risk of fraud[9].

\subsection{Decentralized Autonomous Organizations}
Decentralized Autonomous Organizations (DAOs) use the blockchain and smart contracts as a way to govern and operate an organization without a central authority. DAOs allow participants to vote on proposed policy changes, actions taken by the organization, and any number of other decisions. These rules are automatically enforced by smart contracts. The first notable DAO, “The DAO” was formed on the Ethereum blockchain in 2016 as a venture capital fund. Users could exchange ether for tokens that gave holders voting power in The DAO proportional to the amount of tokens owned[10]. The organization managed to crowdfund \$168M worth of ether representing one of the largest projects on the Ethereum blockchain. The project is now synonymous with a programming vulnerability in the organization's smart contract that allowed an attacker to siphon off \$50M from The DAO’s[11] gathered funds. This resulted in the controversial hard fork of the Ethereum blockchain and the shuttering of the organization. This example highlights the critical nature of DAO smart contract security as they manage large amounts of currency and interact with a large number of users. Today, a great variety of DAOs exist on Ethereum ranging from communities of creators to venture capital groups[12].

\section{Threat Model}
DAO contract voting vulnerabilities refers to a class of vulnerabilities where an attacker exploits the contract voting mechanism to vote twice with the same tokens, remove other people's votes, vote on a proposal and immediately put it into effect without giving other token holders a chance to vote themselves, or other similar exploits that undermine the decentralized democratic goals of DAO contracts. In our analysis, we assume that attackers have complete visibility of the contract code, and the ability to deploy their own contracts to the blockchain that interface with DAO contracts[13]; however, we are assuming that attackers cannot launch larger Ethereum network attacks such as network congestion or miner manipulation that would require greater coordination and resources. We consider nonvoting-related attacks such as integer overflow, reentrancy, and gas DoS attacks as out of scope for this paper.

\section{Design}
\subsection{Defining security properties for DAO smart contracts}
\begin{center}
\begin{tikzpicture}[scale=0.15]
\tikzstyle{every node}+=[inner sep=0pt]
\draw [black] (9,-32.6) circle (3);
\draw (9,-32.6) node {$s_1,s_2$};
\draw [black] (23.6,-16) circle (3);
\draw (23.6,-16) node {$D_1$};
\draw [black] (23.6,-49.3) circle (3);
\draw (23.6,-49.3) node {$W_1$};
\draw [black] (42.4,-16) circle (3);
\draw (42.4,-16) node {$D_2$};
\draw [black] (57.2,-16) circle (3);
\draw (57.2,-16) node {$D_3$};
\draw [black] (43.6,-49.3) circle (3);
\draw (43.6,-49.3) node {$W_2$};
\draw [black] (57.2,-49.3) circle (3);
\draw (57.2,-49.3) node {$W_3$};
\draw [black] (46.4,-32.6) circle (3);
\draw (46.4,-32.6) node {$I$};
\draw [black] (28.7,-32.6) circle (3);
\draw (28.7,-32.6) node {$R$};
\draw [black] (10.98,-30.35) -- (21.62,-18.25);
\fill [black] (21.62,-18.25) -- (20.71,-18.52) -- (21.47,-19.18);
\draw (16.84,-25.75) node [right] {$a_1$};
\draw [black] (10.97,-34.86) -- (21.63,-47.04);
\fill [black] (21.63,-47.04) -- (21.48,-46.11) -- (20.72,-46.77);
\draw (16.84,-39.5) node [right] {$a_2$};
\draw [black] (26.6,-16) -- (39.4,-16);
\fill [black] (39.4,-16) -- (38.6,-15.5) -- (38.6,-16.5);
\draw (33,-16.5) node [below] {$c_1$};
\draw [black] (45.4,-16) -- (54.2,-16);
\fill [black] (54.2,-16) -- (53.4,-15.5) -- (53.4,-16.5);
\draw (49.8,-16.5) node [below] {$d_1$};
\draw [black] (26.6,-49.3) -- (40.6,-49.3);
\fill [black] (40.6,-49.3) -- (39.8,-48.8) -- (39.8,-49.8);
\draw (33.6,-49.8) node [below] {$c_2$};
\draw [black] (46.6,-49.3) -- (54.2,-49.3);
\fill [black] (54.2,-49.3) -- (53.4,-48.8) -- (53.4,-49.8);
\draw (50.4,-49.8) node [below] {$d_2$};
\draw [black] (8.934,-29.602) arc (-182.00565:-319.9871:26.325);
\fill [black] (8.93,-29.6) -- (9.46,-28.82) -- (8.46,-28.79);
\draw [black] (55.065,-51.406) arc (-48.49526:-169.72438:27.748);
\fill [black] (9.37,-35.58) -- (9.03,-36.45) -- (10.01,-36.27);
\draw [black] (43.4,-32.6) -- (31.7,-32.6);
\fill [black] (31.7,-32.6) -- (32.5,-33.1) -- (32.5,-32.1);
\draw (37.55,-33.1) node [below] {$f$};
\draw [black] (24.48,-18.87) -- (27.82,-29.73);
\fill [black] (27.82,-29.73) -- (28.06,-28.82) -- (27.11,-29.11);
\draw (25.38,-24.93) node [left] {$b_1$};
\draw [black] (24.48,-46.43) -- (27.82,-35.47);
\fill [black] (27.82,-35.47) -- (27.11,-36.09) -- (28.07,-36.38);
\draw (26.92,-41.57) node [right] {$b_2$};
\draw [black] (43.1,-18.92) -- (45.7,-29.68);
\fill [black] (45.7,-29.68) -- (46,-28.79) -- (45.02,-29.02);
\draw (43.64,-24.73) node [left] {$e_1$};
\draw [black] (44.1,-46.34) -- (45.9,-35.56);
\fill [black] (45.9,-35.56) -- (45.28,-36.27) -- (46.26,-36.43);
\draw (45.71,-41.18) node [right] {$e_2$};
\end{tikzpicture}
\end{center}

\section{Approach}
Our approach uses Scribble and Mythril together to formally verify critical correctness properties in Ethereum-based DAO voting contracts. To begin, we identify essential governance rules found in most DAO implementations and articulate them into specific safety and liveness properties. Some key requirements include only token holders being able to vote, as well as prevention of double counting votes. These rules are expressed through Scribble annotations, which convert informal governance assumptions into precise assertions that are embedded into the Solidity contract.

Our verification approach targets three core properties critical to DAO smart contract security. First, we verify Single Vote Enforcement, confirming that each member is restricted to casting only one vote per proposal, preventing potential manipulation through multiple votes. Second, we ensure Authorized Access, validating that voting and proposal functionalities are limited exclusively to authorized DAO members, thus safeguarding against unauthorized interference. Lastly, we confirm Integrity of Proposal Outcome, ensuring the correctness and immutability of voting results once finalized, to protect decision-making from fraudulent or erroneous alterations. We annotate each property explicitly using Scribble, enabling Mythril to systematically verify these essential conditions.

Once the properties are specified, we recompile the smart contract code using Scribble, then analyze it using Mythril’s symbolic execution engine. Mythril traverses possible execution paths, trying to invalidate the assertions that were defined earlier. If any violation is discovered by Mythril, it returns a counterexample and a symbolic execution path that led to the issue.

Upon encountering counterexamples, we analyze whether these findings represent genuine logic flaws or overly restrictive specifications. If there is a genuine logic flaw, we will flag it for review, while the latter will cause us to refine our annotations. We will evaluate the performance of our verification framework by testing it on both authentic DAO contracts and synthetic contracts that are injected with known vulnerabilities. Our goal is to produce a streamlined workflow that runs lightweight yet rigorous annotation-driven formal verification to ensure that Ethereum-based DAO governance contracts are secure.

We will first test synthetically vulnerable smart contracts specifically designed to contain known security flaws related to DAO voting. This initial step allows us to validate the correctness of our verification techniques in detecting deliberate vulnerabilities. After establishing confidence in our methodology, we will progress to analyzing a realistic and manageable contract such as MolochDAO v2[14], to test our verification framework in a practical but simplified real-world scenario.

We began by successfully setting up Mythril and integrating Scribble annotations for formal verification. To validate our setup, we created a simplified DAO smart contract example, incorporating core DAO functionalities. We annotated the critical sections using Scribble to define security properties explicitly. Running Mythril against this annotated DAO allowed us to verify that our environment and workflow operate correctly, establishing a solid foundation for further verification of more complex real-world DAOs.

\section{Evaluation}

This project investigates whether symbolic execution can be used to verify the safety and liveness properties of DAO voting functions. It also explores the scalability of this approach when applied to more complex voting mechanisms and assesses whether the method can be adapted to different DAOs' smart contracts. If automation isn't feasible, we want to investigate the manual effort required for adaptation. Our experiments will involve both toy examples and open-source smart contracts, focusing on analyzing DAO voting logic and defining the properties needed to verify it.

\section{Plan of Work}
We have already begun by studying the relevant tools, Scribble and Mythril, in order to understand the specification language and the way Mythril verifies security properties after they have been defined by Scribble. Next, we wrote a simple DAO contract, defined a security property in Slither, and verified the property using Mythril as an end-to-end test of our research procedure. We will go on to define security properties for each voting vulnerability in each smart contract that we plan to test. Over the next week we will verify the first three DAO contracts in our suite, and then in the final week we will verify the last two along with our final write-up. Our expected goal is to verify three different security properties in these five contracts. Our stretch goal would be to verify these properties in 10 contracts, but at minimum we expect to fully verify these properties in three contracts from our test suite.

\section{Who Did What}
\begin{itemize}
    \item Aidan: Contributed to the Introduction, Threat Model, and References
    \item Anish: Contributed to the Approach, Set up repository, dependencies, and starter DAO contract/annotations
    \item Jeffrey: Contributed to the Background, State of the Art, and Evaluation sections
\end{itemize}

\begin{thebibliography}{00}
\bibitem{b1} J. Feist, G. Grieco, and A. Groce, “Slither: A static analysis framework for smart contracts,” 2019, pp. 8–15. doi: https://doi.org/10.1109/WETSEB.2019.00008. Available: \url{https://ieeexplore.ieee.org/abstract/document/8823898?casa_token=SNthQs5W2d0AAAAA:XwX332JMCkj3hw8XZd9nKBxe2bKJZ3v3yUNJ3jPtangZ3L2nISxh_rbY8fBW2zXkaWa0QnqgqVE}
\bibitem{b2} Z. Nehaï, P.-Y. Piriou, and F. Daumas, “Model-checking of smart contracts,” 2018, pp. 980–987. Available: \url{https://ieeexplore.ieee.org/abstract/document/8726806}
\bibitem{b3} J. He, M. Balunović, N. Ambroladze, P. Tsankov, and M. Vechev, “Learning to Fuzz from Symbolic Execution with Application to Smart Contracts,” Proceedings of the 2019 ACM SIGSAC Conference on Computer and Communications Security, pp. 531–548, Nov. 2019, Available: \url{https://dl.acm.org/doi/abs/10.1145/3319535.3363230?casa_token=5cBcZneJt7oAAAAA:sPluGu-gtO_db3qLqHUcylo4ksy4Rx0FBkiEBFom7You4VltkgLyZanIwgg-WHfLDVmrwmU0MbdpGA}
\bibitem{b4} N. Sharma and S. Sharma, “A Survey of Mythril, A Smart Contract Security Analysis Tool for EVM Bytecode,” Indian Journal of Natural Sciences, vol. 12, no. 75, Dec. 2022, Available:
\url{https://www.researchgate.net/profile/Swati-Sharma-171/publication/366391033_A_Survey_of_Mythril_A_Smart_Contract_Security_Analysis_Tool_for_EVM_Bytecode/links/639ecbdc095a6a77743c8073/A-Survey-of-Mythril-A-Smart-Contract-Security-Analysis-Tool-for-EVM-Bytecode.pdf}
\bibitem{b5} ConsenSysDiligence, “GitHub - ConsenSysDiligence/scribble: Scribble instrumentation tool,” GitHub, Apr. 09, 2025. Available:  
\url{ConsenSysDiligence, “GitHub - ConsenSysDiligence/scribble: Scribble instrumentation tool,” GitHub, Apr. 09, 2025. https://github.com/ConsenSysDiligence/scribble/tree/develop (accessed Apr. 10, 2025).}
\bibitem{6} S. Nakamoto, “Bitcoin: a Peer-to-Peer Electronic Cash System,” bitcoin.org, Oct. 2008. Available: 
\url{https://bitcoin.org/bitcoin.pdf}
\bibitem{7} V. Buterin, “Ethereum Whitepaper,” Ethereum, 2014. Available: 
\url{https://ethereum.org/en/whitepaper/}
\bibitem{8} P. Wackerow, “Introduction to smart contracts,” ethereum.org, Sep. 02, 2022. Available: 
\url{https://ethereum.org/en/developers/docs/smart-contracts/}
\bibitem{9} N. Szabo, “Smart Contracts,” www.fon.hum.uva.nl, 1994. 
\url{https://www.fon.hum.uva.nl/rob/Courses/InformationInSpeech/CDROM/Literature/LOTwinterschool2006/szabo.best.vwh.net/smart.contracts.html}
\bibitem{10} C. Jentzsch, “DECENTRALIZED AUTONOMOUS ORGANIZATION TO AUTOMATE GOVERNANCE,” 2016. Available: 
\url{https://lawofthelevel.lexblogplatformthree.com/wp-content/uploads/sites/187/2017/07/WhitePaper-1.pdf}
\bibitem{11} C. Shier et al., “Understanding a Revolutionary and Flawed Grand Experiment in Blockchain: The DAO Attack,” SSRN Electronic Journal, 2017, doi: 
\url{https://doi.org/10.2139/ssrn.3014782.}
\bibitem{12} “List of 41 DAOs (2025),” Alchemy, 2025. Available:
\url{https://www.alchemy.com/dapps/top/daos}
\bibitem{13} K. Nekrasov, “DAO Voting Vulnerabilities,” Mixbytes.io, 2024.
\url{https://mixbytes.io/blog/dao-voting-vulnerabilities}
\bibitem{14} HausDAO, “GitHub - HausDAO/Molochv2.1: Moloch DAO v2 with multi-summoner capabilities, plus register function for metadata.,” GitHub, 2020. Available:
\url{https://github.com/HausDAO/Molochv2.1}
\end{thebibliography}
\end{document}
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{url}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tikz}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Formally Verifying Voter Security Properties in DAO Smart Contracts}

\author{
    \makebox[\textwidth][c]{%
        \begin{minipage}{0.45\textwidth}
            \centering
            \textbf{Anish Toomu} \\
            \textit{Department of Computer Science} \\
            \textit{University of North Carolina at Chapel Hill} \\
            Chapel Hill, North Carolina, USA
        \end{minipage}
        \hfill
        \begin{minipage}{0.45\textwidth}
            \centering
            \textbf{Aidan Maguire} \\
            \textit{Department of Computer Science} \\
            \textit{University of North Carolina at Chapel Hill} \\
            Chapel Hill, North Carolina, USA
        \end{minipage}
    }\\[1.5em]

    \makebox[\textwidth][c]{%
        \begin{minipage}{0.6\textwidth}
            \centering
            \textbf{Jeffrey Zhang} \\
            \textit{Department of Computer Science} \\
            \textit{University of North Carolina at Chapel Hill} \\
            Chapel Hill, North Carolina, USA
        \end{minipage}
    }
}

\maketitle

\section{Abstract}
To be written

\section{Introduction}
This project aims to make use of two existing security tools to define and verify security properties for voting methods across a suite of Ethereum blockchain programs. Many Ethereum blockchain programs take the form of a DAO, or Decentralized Autonomous Organization, wherein users holding tokens that verify them as members of the organization can spend those tokens to vote on decision-making for the DAO as a whole. There are several types of vulnerabilities that have been identified in these types of contracts, but for this paper we will be looking at vulnerabilities surrounding the vote system that allow attackers to exploit the democratic principles behind DAOs.

Our proposal intends to formally verify a suite of the most used DAO contracts to confirm that they are secure. We will require the use of Scribble, a specification language that allows us to define security properties for DAO contracts as annotations within the contracts themselves. We will then use Mythril, a security-analysis tool, to verify each of our newly defined security properties for our suite of popular contracts. If successful, we will increase the confidence in these widely-used contracts. Possible challenges include the properties not being entirely specifiable in Scribble's specification language, and some contracts being too complex to analyze with Mythril due to state explosion.

\section{State of the Art}

DAOs are a type of smart contract that define the rules and structure of a organization. In more general terms, DAOs represent decentralized communities that can allocate resources without centralized leadership. While there exist tools for various methods of verifying and bug-finding in smart contracts including static analysis[1], model checking[2], and symbolic execution[3], they haven’t been narrowed down to focus on DAOs, and the specific exploits that come with their voting systems, a key, shared property across DAOs and a critical part of their operations. We have chosen to use an existing symbolic execution-based tool, Mythril[4], along with Scribble[5], a specification language for properties in this work.

\section{Background}
To understand our proposed enhancements to Mythril, we must first grasp the fundamental concepts of the blockchain, the Ethereum blockchain and its innovative smart contracts, and finally DAOs, a subset of smart contracts with common functionalities.

\subsection{Blockchain}
A blockchain serves as a ledger of transactions that is transparent, decentralized, and secure. Each block in the chain contains information about transactions allowing anyone to inspect them at any time. Additionally, each block contains a cryptographic hash of the previous block in the chain. This chain means that in the event of a block being tampered with by an attacker, all of the altered blocks' successors would also be changed. The consensus needed to accept a chain also provides further security. If the majority of the computational power on the network is controlled by honest parties then the honest chain will be accepted. An attacker seeking to change a block would need to alter the block, redo all the proof-of-work computation for it and its successor blocks, and then catch up to the honest chain to be accepted. This proves to be computationally infeasible[6].

\subsection{Ethereum and Smart Contracts}
Ethereum, as proposed by Vitalik Buterin in 2014, seeks to provide an alternative to Bitcoin with a focus on the development of decentralized applications. This is achieved through a blockchain that contains a built-in Turing-complete language[7]. This language allows users to write smart contracts that are stored on the blockchain. Smart contracts are a type of account, they have a balance and can be interacted with through transactions. They differ from users’ externally owned accounts in their method of control. Where externally owned accounts are controlled by user decisions, smart contracts are programs that run on the blockchain according to their code. Users or other smart contracts interact with smart contracts by sending a transaction that executes the functions defined by the contract’s code. Smart contracts automatically execute when their conditions are met, are universally visible, and are unable to be changed once uploaded[8]. In this way smart contracts provide a trustworthy, automated way to enforce agreements, reducing the need for third-party enforcement, minimizing exceptions, and lowering the risk of fraud[9].

\subsection{Decentralized Autonomous Organizations}
Decentralized Autonomous Organizations (DAOs) use the blockchain and smart contracts as a way to govern and operate an organization without a central authority. DAOs allow participants to vote on proposed policy changes, actions taken by the organization, and any number of other decisions. These rules are automatically enforced by smart contracts. The first notable DAO, “The DAO” was formed on the Ethereum blockchain in 2016 as a venture capital fund. Users could exchange ether for tokens that gave holders voting power in The DAO proportional to the amount of tokens owned[10]. The organization managed to crowdfund \$168M worth of ether representing one of the largest projects on the Ethereum blockchain. The project is now synonymous with a programming vulnerability in the organization's smart contract that allowed an attacker to siphon off \$50M from The DAO’s[11] gathered funds. This resulted in the controversial hard fork of the Ethereum blockchain and the shuttering of the organization. This example highlights the critical nature of DAO smart contract security as they manage large amounts of currency and interact with a large number of users. Today, a great variety of DAOs exist on Ethereum ranging from communities of creators to venture capital groups[12].

\section{Threat Model}
DAO contract voting vulnerabilities refers to a class of vulnerabilities where an attacker exploits the contract voting mechanism to vote twice with the same tokens, remove other people's votes, vote on a proposal and immediately put it into effect without giving other token holders a chance to vote themselves, or other similar exploits that undermine the decentralized democratic goals of DAO contracts. In our analysis, we assume that attackers have complete visibility of the contract code, and the ability to deploy their own contracts to the blockchain that interface with DAO contracts[13]; however, we are assuming that attackers cannot launch larger Ethereum network attacks such as network congestion or miner manipulation that would require greater coordination and resources. We consider nonvoting-related attacks such as integer overflow, reentrancy, and gas DoS attacks as out of scope for this paper.

\section{Design}

\subsection{A Formal Model of DAO Smart Contracts}
There is not a prescriptive structure that smart contracts must conform to in order to be considered DAOs, but there are some functionalities that are common to all implementations. All DAOs have a voting function in their contract that allows members to vote on proposals made by other members. We represent the general form of this voting function as a finite state machine that DAO members can interact with. We define the FSM as follows:
\begin{center}
$M = (Q, \Sigma, \delta, q_0, F)$
\end{center}

With $Q$ being the set of contract states, $\Sigma$ being the set of events, $\delta$ being the transition function mapping $Q\times\Sigma$, $q_0$ being the initial state, and $F$ being the set of terminal states. 
We define the set $Q$ as follows:
\begin{center}
\begin{tabular}{|c|c|}
\hline
State & Description\\
\hline
$q_0$ & Initial state. Contract is inert.\\
\hline
A & Vote request initiated. Voter identity set\\
\hline
B & Vote request validated\\
\hline
Y & Vote total updated in favor. Terminate interaction \\
\hline
N & Vote total updated against. Terminate interaction\\
\hline
R & Vote canceled. Terminate interaction\\
\hline
\end{tabular}
\end{center}

And define the set $Sigma$ as follows:
\begin{center}
\begin{tabular}{|c|c|}
\hline
Event & Description\\
\hline
Vote function called & Member makes request to contract\\
\hline
Vote validated & Vote request validated (explained below)\\
\hline
Vote yes & Member votes in favor \\
\hline
Vote no & Member votes against\\
\hline
Vote rejected & Vote request is invalid (explained below)\\
\hline
\end{tabular}
\end{center}

And finally provide a diagram of the finite state machine.
\begin{center}
\begin{tikzpicture}[scale=0.2]
\tikzstyle{every node}+=[inner sep=0pt]
\draw [black] (36.9,-9.6) circle (3);
\draw (36.9,-9.6) node {$q_0$};
\draw [black] (36.9,-22) circle (3);
\draw (36.9,-22) node {$A$};
\draw [black] (36.9,-33.6) circle (3);
\draw (36.9,-33.6) node {$B$};
\draw [black] (55.8,-22) circle (3);
\draw (55.8,-22) node {$R$};
\draw [black] (55.8,-22) circle (2.4);
\draw [black] (45.7,-45.7) circle (3);
\draw (45.7,-45.7) node {$N$};
\draw [black] (45.7,-45.7) circle (2.4);
\draw [black] (28.3,-45.7) circle (3);
\draw (28.3,-45.7) node {$Y$};
\draw [black] (28.3,-45.7) circle (2.4);
\draw [black] (36.9,-12.6) -- (36.9,-19);
\fill [black] (36.9,-19) -- (37.4,-18.2) -- (36.4,-18.2);
\draw (36.4,-15.8) node [left] {$Vote\mbox{ }function\mbox{ }called$};
\draw [black] (36.9,-25) -- (36.9,-30.6);
\fill [black] (36.9,-30.6) -- (37.4,-29.8) -- (36.4,-29.8);
\draw (36.4,-27.8) node [left] {$Vote\mbox{ }validated$};
\draw [black] (39.9,-22) -- (52.8,-22);
\fill [black] (52.8,-22) -- (52,-21.5) -- (52,-22.5);
\draw (46.35,-22.5) node [below] {$Vote\mbox{ }rejected$};
\draw [black] (38.66,-36.03) -- (43.94,-43.27);
\fill [black] (43.94,-43.27) -- (43.87,-42.33) -- (43.06,-42.92);
\draw (41.89,-38.27) node [right] {$Vote\mbox{ }no$};
\draw [black] (35.16,-36.05) -- (30.04,-43.25);
\fill [black] (30.04,-43.25) -- (30.91,-42.89) -- (30.09,-42.31);
\draw (32.01,-38.28) node [left] {$Vote\mbox{ }yes$};
\end{tikzpicture}
\end{center}

This formal model provides the foundation for our conception of DAO smart contracts. As our goal is to verify the voting functionality of DAOs, it follows that we are focused primarily on the \textit{Vote Validated} event transition, and this is where most of our verification efforts will take place. Defining what it means for a vote to be validated will lead us to introduce our security properties.

\subsection{Security Properties for Secure DAO Voting}

\section{Approach}
Our approach uses Scribble and Mythril together to formally verify critical correctness properties in Ethereum-based DAO voting contracts. To begin, we identify essential governance rules found in most DAO implementations and articulate them into specific safety and liveness properties. Some key requirements include only token holders being able to vote, as well as prevention of double counting votes. These rules are expressed through Scribble annotations, which convert informal governance assumptions into precise assertions that are embedded into the Solidity contract.

Our verification approach targets three core properties critical to DAO smart contract security. First, we verify Single Vote Enforcement, confirming that each member is restricted to casting only one vote per proposal, preventing potential manipulation through multiple votes. Second, we ensure Authorized Access, validating that voting and proposal functionalities are limited exclusively to authorized DAO members, thus safeguarding against unauthorized interference. Lastly, we confirm Integrity of Proposal Outcome, ensuring the correctness and immutability of voting results once finalized, to protect decision-making from fraudulent or erroneous alterations. We annotate each property explicitly using Scribble, enabling Mythril to systematically verify these essential conditions.

Once the properties are specified, we recompile the smart contract code using Scribble, then analyze it using Mythril’s symbolic execution engine. Mythril traverses possible execution paths, trying to invalidate the assertions that were defined earlier. If any violation is discovered by Mythril, it returns a counterexample and a symbolic execution path that led to the issue.

Upon encountering counterexamples, we analyze whether these findings represent genuine logic flaws or overly restrictive specifications. If there is a genuine logic flaw, we will flag it for review, while the latter will cause us to refine our annotations. We will evaluate the performance of our verification framework by testing it on both authentic DAO contracts and synthetic contracts that are injected with known vulnerabilities. Our goal is to produce a streamlined workflow that runs lightweight yet rigorous annotation-driven formal verification to ensure that Ethereum-based DAO governance contracts are secure.

We will first test synthetically vulnerable smart contracts specifically designed to contain known security flaws related to DAO voting. This initial step allows us to validate the correctness of our verification techniques in detecting deliberate vulnerabilities. After establishing confidence in our methodology, we will progress to analyzing a realistic and manageable contract such as MolochDAO v2[14], to test our verification framework in a practical but simplified real-world scenario.

We began by successfully setting up Mythril and integrating Scribble annotations for formal verification. To validate our setup, we created a simplified DAO smart contract example, incorporating core DAO functionalities. We annotated the critical sections using Scribble to define security properties explicitly. Running Mythril against this annotated DAO allowed us to verify that our environment and workflow operate correctly, establishing a solid foundation for further verification of more complex real-world DAOs.

\section{Implementation}
To be written

\section{Evaluation}

This project investigates whether symbolic execution can be used to verify the safety and liveness properties of DAO voting functions. It also explores the scalability of this approach when applied to more complex voting mechanisms and assesses whether the method can be adapted to different DAOs' smart contracts. If automation isn't feasible, we want to investigate the manual effort required for adaptation. Our experiments will involve both toy examples and open-source smart contracts, focusing on analyzing DAO voting logic and defining the properties needed to verify it.

\section{Conclusion}
To be written

\section{Who Did What}
\begin{itemize}
    \item Aidan: Contributed to the Introduction, Threat Model, and References
    \item Anish: Contributed to the Approach, Set up repository, dependencies, and starter DAO contract/annotations
    \item Jeffrey: Contributed to the Background, State of the Art, and Evaluation sections
\end{itemize}

\begin{thebibliography}{00}
\bibitem{b1} J. Feist, G. Grieco, and A. Groce, “Slither: A static analysis framework for smart contracts,” 2019, pp. 8–15. doi: https://doi.org/10.1109/WETSEB.2019.00008. Available: \url{https://ieeexplore.ieee.org/abstract/document/8823898?casa_token=SNthQs5W2d0AAAAA:XwX332JMCkj3hw8XZd9nKBxe2bKJZ3v3yUNJ3jPtangZ3L2nISxh_rbY8fBW2zXkaWa0QnqgqVE}
\bibitem{b2} Z. Nehaï, P.-Y. Piriou, and F. Daumas, “Model-checking of smart contracts,” 2018, pp. 980–987. Available: \url{https://ieeexplore.ieee.org/abstract/document/8726806}
\bibitem{b3} J. He, M. Balunović, N. Ambroladze, P. Tsankov, and M. Vechev, “Learning to Fuzz from Symbolic Execution with Application to Smart Contracts,” Proceedings of the 2019 ACM SIGSAC Conference on Computer and Communications Security, pp. 531–548, Nov. 2019, Available: \url{https://dl.acm.org/doi/abs/10.1145/3319535.3363230?casa_token=5cBcZneJt7oAAAAA:sPluGu-gtO_db3qLqHUcylo4ksy4Rx0FBkiEBFom7You4VltkgLyZanIwgg-WHfLDVmrwmU0MbdpGA}
\bibitem{b4} N. Sharma and S. Sharma, “A Survey of Mythril, A Smart Contract Security Analysis Tool for EVM Bytecode,” Indian Journal of Natural Sciences, vol. 12, no. 75, Dec. 2022, Available:
\url{https://www.researchgate.net/profile/Swati-Sharma-171/publication/366391033_A_Survey_of_Mythril_A_Smart_Contract_Security_Analysis_Tool_for_EVM_Bytecode/links/639ecbdc095a6a77743c8073/A-Survey-of-Mythril-A-Smart-Contract-Security-Analysis-Tool-for-EVM-Bytecode.pdf}
\bibitem{b5} ConsenSysDiligence, “GitHub - ConsenSysDiligence/scribble: Scribble instrumentation tool,” GitHub, Apr. 09, 2025. Available:  
\url{ConsenSysDiligence, “GitHub - ConsenSysDiligence/scribble: Scribble instrumentation tool,” GitHub, Apr. 09, 2025. https://github.com/ConsenSysDiligence/scribble/tree/develop (accessed Apr. 10, 2025).}
\bibitem{6} S. Nakamoto, “Bitcoin: a Peer-to-Peer Electronic Cash System,” bitcoin.org, Oct. 2008. Available: 
\url{https://bitcoin.org/bitcoin.pdf}
\bibitem{7} V. Buterin, “Ethereum Whitepaper,” Ethereum, 2014. Available: 
\url{https://ethereum.org/en/whitepaper/}
\bibitem{8} P. Wackerow, “Introduction to smart contracts,” ethereum.org, Sep. 02, 2022. Available: 
\url{https://ethereum.org/en/developers/docs/smart-contracts/}
\bibitem{9} N. Szabo, “Smart Contracts,” www.fon.hum.uva.nl, 1994. 
\url{https://www.fon.hum.uva.nl/rob/Courses/InformationInSpeech/CDROM/Literature/LOTwinterschool2006/szabo.best.vwh.net/smart.contracts.html}
\bibitem{10} C. Jentzsch, “DECENTRALIZED AUTONOMOUS ORGANIZATION TO AUTOMATE GOVERNANCE,” 2016. Available: 
\url{https://lawofthelevel.lexblogplatformthree.com/wp-content/uploads/sites/187/2017/07/WhitePaper-1.pdf}
\bibitem{11} C. Shier et al., “Understanding a Revolutionary and Flawed Grand Experiment in Blockchain: The DAO Attack,” SSRN Electronic Journal, 2017, doi: 
\url{https://doi.org/10.2139/ssrn.3014782.}
\bibitem{12} “List of 41 DAOs (2025),” Alchemy, 2025. Available:
\url{https://www.alchemy.com/dapps/top/daos}
\bibitem{13} K. Nekrasov, “DAO Voting Vulnerabilities,” Mixbytes.io, 2024.
\url{https://mixbytes.io/blog/dao-voting-vulnerabilities}
\bibitem{14} HausDAO, “GitHub - HausDAO/Molochv2.1: Moloch DAO v2 with multi-summoner capabilities, plus register function for metadata.,” GitHub, 2020. Available:
\url{https://github.com/HausDAO/Molochv2.1}
\end{thebibliography}
\end{document}

### 2025-04-27 paper.tex
tracking paper

@@
 \end{document}
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
-\usepackage{url}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{xcolor}
-\usepackage{tikz}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Formally Verifying Voter Security Properties in DAO Smart Contracts}
-
-\author{
-    \makebox[\textwidth][c]{%
-        \begin{minipage}{0.45\textwidth}
-            \centering
-            \textbf{Anish Toomu} \\
-            \textit{Department of Computer Science} \\
-            \textit{University of North Carolina at Chapel Hill} \\
-            Chapel Hill, North Carolina, USA
-        \end{minipage}
-        \hfill
-        \begin{minipage}{0.45\textwidth}
-            \centering
-            \textbf{Aidan Maguire} \\
-            \textit{Department of Computer Science} \\
-            \textit{University of North Carolina at Chapel Hill} \\
-            Chapel Hill, North Carolina, USA
-        \end{minipage}
-    }\\[1.5em]
-
-    \makebox[\textwidth][c]{%
-        \begin{minipage}{0.6\textwidth}
-            \centering
-            \textbf{Jeffrey Zhang} \\
-            \textit{Department of Computer Science} \\
-            \textit{University of North Carolina at Chapel Hill} \\
-            Chapel Hill, North Carolina, USA
-        \end{minipage}
-    }
-}
-
-\maketitle
-
-\section{Abstract}
-To be written
-
-\section{Introduction}
-This project aims to make use of two existing security tools to define and verify security properties for voting methods across a suite of Ethereum blockchain programs.
-Many Ethereum blockchain programs take the form of a DAO, or Decentralized Autonomous Organization, wherein users holding tokens that verify them as members of the organization can spend those tokens to vote on decision-making for the DAO as a whole.
-There are several types of vulnerabilities that have been identified in these types of contracts, but for this paper we will be looking at vulnerabilities surrounding the vote system that allow attackers to exploit the democratic principles behind DAOs.
-
-Our proposal intends to formally verify a suite of the most used DAO contracts to confirm that they are secure.
-We will require the use of Scribble, a specification language that allows us to define security properties for DAO contracts as annotations within the contracts themselves.
-We will then use Mythril, a security-analysis tool, to verify each of our newly defined security properties for our suite of popular contracts.
-If successful, we will increase the confidence in these widely-used contracts.
-Possible challenges include the properties not being entirely specifiable in Scribble's specification language, and some contracts being too complex to analyze with Mythril due to state explosion.
-
-\section{State of the Art}
-
-DAOs are a type of smart contract that define the rules and structure of a organization.
-In more general terms, DAOs represent decentralized communities that can allocate resources without centralized leadership.
-While there exist tools for various methods of verifying and bug-finding in smart contracts including static analysis[1], model checking[2], and symbolic execution[3], they haven’t been narrowed down to focus on DAOs, and the specific exploits that come with their voting systems, a key, shared property across DAOs and a critical part of their operations.
-We have chosen to use an existing symbolic execution-based tool, Mythril[4], along with Scribble[5], a specification language for properties in this work.
-
-\section{Background}
-To understand our proposed enhancements to Mythril, we must first grasp the fundamental concepts of the blockchain, the Ethereum blockchain and its innovative smart contracts, and finally DAOs, a subset of smart contracts with common functionalities.
-
-\subsection{Blockchain}
-A blockchain serves as a ledger of transactions that is transparent, decentralized, and secure.
-Each block in the chain contains information about transactions allowing anyone to inspect them at any time.
-Additionally, each block contains a cryptographic hash of the previous block in the chain.
-This chain means that in the event of a block being tampered with by an attacker, all of the altered blocks' successors would also be changed.
-The consensus needed to accept a chain also provides further security.
-If the majority of the computational power on the network is controlled by honest parties then the honest chain will be accepted.
-An attacker seeking to change a block would need to alter the block, redo all the proof-of-work computation for it and its successor blocks, and then catch up to the honest chain to be accepted.
-This proves to be computationally infeasible[6].
-
-\subsection{Ethereum and Smart Contracts}
-Ethereum, as proposed by Vitalik Buterin in 2014, seeks to provide an alternative to Bitcoin with a focus on the development of decentralized applications.
-This is achieved through a blockchain that contains a built-in Turing-complete language[7].
-This language allows users to write smart contracts that are stored on the blockchain.
-Smart contracts are a type of account, they have a balance and can be interacted with through transactions.
-They differ from users’ externally owned accounts in their method of control.
-Where externally owned accounts are controlled by user decisions, smart contracts are programs that run on the blockchain according to their code.
-Users or other smart contracts interact with smart contracts by sending a transaction that executes the functions defined by the contract’s code.
-Smart contracts automatically execute when their conditions are met, are universally visible, and are unable to be changed once uploaded[8].
-In this way smart contracts provide a trustworthy, automated way to enforce agreements, reducing the need for third-party enforcement, minimizing exceptions, and lowering the risk of fraud[9].
-
-\subsection{Decentralized Autonomous Organizations}
-Decentralized Autonomous Organizations (DAOs) use the blockchain and smart contracts as a way to govern and operate an organization without a central authority.
-DAOs allow participants to vote on proposed policy changes, actions taken by the organization, and any number of other decisions.
-These rules are automatically enforced by smart contracts.
-The first notable DAO, “The DAO” was formed on the Ethereum blockchain in 2016 as a venture capital fund.
-Users could exchange ether for tokens that gave holders voting power in The DAO proportional to the amount of tokens owned[10].
-The organization managed to crowdfund \$168M worth of ether representing one of the largest projects on the Ethereum blockchain.
-The project is now synonymous with a programming vulnerability in the organization's smart contract that allowed an attacker to siphon off \$50M from The DAO’s[11] gathered funds.
-This resulted in the controversial hard fork of the Ethereum blockchain and the shuttering of the organization.
-This example highlights the critical nature of DAO smart contract security as they manage large amounts of currency and interact with a large number of users.
-Today, a great variety of DAOs exist on Ethereum ranging from communities of creators to venture capital groups[12].
-
-\section{Threat Model}
-DAO contract voting vulnerabilities refers to a class of vulnerabilities where an attacker exploits the contract voting mechanism to vote twice with the same tokens, remove other people's votes, vote on a proposal and immediately put it into effect without giving other token holders a chance to vote themselves, or other similar exploits that undermine the decentralized democratic goals of DAO contracts.
-In our analysis, we assume that attackers have complete visibility of the contract code, and the ability to deploy their own contracts to the blockchain that interface with DAO contracts[13]; however, we are assuming that attackers cannot launch larger Ethereum network attacks such as network congestion or miner manipulation that would require greater coordination and resources.
-We consider nonvoting-related attacks such as integer overflow, reentrancy, and gas DoS attacks as out of scope for this paper.
-
-\section{Design}
-
-\subsection{A Formal Model of DAO Smart Contracts}
-There is not a prescriptive structure that smart contracts must conform to in order to be considered DAOs, but there are some functionalities that are common to all implementations.
-All DAOs have a voting function in their contract that allows members to vote on proposals made by other members.
-We represent the general form of this voting function as a finite state machine that DAO members can interact with.
-We define the FSM as follows:
-\begin{center}
-$M = (Q, \Sigma, \delta, q_0, F)$
-\end{center}
-
-With $Q$ being the set of contract states, $\Sigma$ being the set of events, $\delta$ being the transition function mapping $Q\times\Sigma$, $q_0$ being the initial state, and $F$ being the set of terminal states.
-We define the set $Q$ as follows:
-\begin{center}
-\begin{tabular}{|c|c|}
-\hline
-State & Description\\
-\hline
-$q_0$ & Initial state. Contract is inert.\\
-\hline
-A & Vote request initiated. Voter identity set\\
-\hline
-B & Vote request validated\\
-\hline
-Y & Vote total updated in favor. Terminate interaction \\
-\hline
-N & Vote total updated against. Terminate interaction\\
-\hline
-R & Vote canceled. Terminate interaction\\
-\hline
-\end{tabular}
-\end{center}
-
-And define the set $Sigma$ as follows:
-\begin{center}
-\begin{tabular}{|c|c|}
-\hline
-Event & Description\\
-\hline
-Vote function called & Member makes request to contract\\
-\hline
-Vote validated & Vote request validated (explained below)\\
-\hline
-Vote yes & Member votes in favor \\
-\hline
-Vote no & Member votes against\\
-\hline
-Vote rejected & Vote request is invalid (explained below)\\
-\hline
-\end{tabular}
-\end{center}
-
-And finally provide a diagram of the finite state machine.
-\begin{center}
-\begin{tikzpicture}[scale=0.2]
-\tikzstyle{every node}+=[inner sep=0pt]
-\draw [black] (36.9,-9.6) circle (3);
-\draw (36.9,-9.6) node {$q_0$};
-\draw [black] (36.9,-22) circle (3);
-\draw (36.9,-22) node {$A$};
-\draw [black] (36.9,-33.6) circle (3);
-\draw (36.9,-33.6) node {$B$};
-\draw [black] (55.8,-22) circle (3);
-\draw (55.8,-22) node {$R$};
-\draw [black] (55.8,-22) circle (2.4);
-\draw [black] (45.7,-45.7) circle (3);
-\draw (45.7,-45.7) node {$N$};
-\draw [black] (45.7,-45.7) circle (2.4);
-\draw [black] (28.3,-45.7) circle (3);
-\draw (28.3,-45.7) node {$Y$};
-\draw [black] (28.3,-45.7) circle (2.4);
-\draw [black] (36.9,-12.6) -- (36.9,-19);
-\fill [black] (36.9,-19) -- (37.4,-18.2) -- (36.4,-18.2);
-\draw (36.4,-15.8) node [left] {$Vote\mbox{ }function\mbox{ }called$};
-\draw [black] (36.9,-25) -- (36.9,-30.6);
-\fill [black] (36.9,-30.6) -- (37.4,-29.8) -- (36.4,-29.8);
-\draw (36.4,-27.8) node [left] {$Vote\mbox{ }validated$};
-\draw [black] (39.9,-22) -- (52.8,-22);
-\fill [black] (52.8,-22) -- (52,-21.5) -- (52,-22.5);
-\draw (46.35,-22.5) node [below] {$Vote\mbox{ }rejected$};
-\draw [black] (38.66,-36.03) -- (43.94,-43.27);
-\fill [black] (43.94,-43.27) -- (43.87,-42.33) -- (43.06,-42.92);
-\draw (41.89,-38.27) node [right] {$Vote\mbox{ }no$};
-\draw [black] (35.16,-36.05) -- (30.04,-43.25);
-\fill [black] (30.04,-43.25) -- (30.91,-42.89) -- (30.09,-42.31);
-\draw (32.01,-38.28) node [left] {$Vote\mbox{ }yes$};
-\end{tikzpicture}
-\end{center}
-
-This formal model provides the foundation for our conception of DAO smart contracts.
-As our goal is to verify the voting functionality of DAOs, it follows that we are focused primarily on the \textit{Vote Validated} event transition, and this is where most of our verification efforts will take place.
-Defining what it means for a vote to be validated will lead us to introduce our security properties.
-
-\subsection{Security Properties for Secure DAO Voting}
-
-\section{Approach}
-Our approach uses Scribble and Mythril together to formally verify critical correctness properties in Ethereum-based DAO voting contracts.
-To begin, we identify essential governance rules found in most DAO implementations and articulate them into specific safety and liveness properties.
-Some key requirements include only token holders being able to vote, as well as prevention of double counting votes.
-These rules are expressed through Scribble annotations, which convert informal governance assumptions into precise assertions that are embedded into the Solidity contract.
-
-Our verification approach targets three core properties critical to DAO smart contract security.
-First, we verify Single Vote Enforcement, confirming that each member is restricted to casting only one vote per proposal, preventing potential manipulation through multiple votes.
-Second, we ensure Authorized Access, validating that voting and proposal functionalities are limited exclusively to authorized DAO members, thus safeguarding against unauthorized interference.
-Lastly, we confirm Integrity of Proposal Outcome, ensuring the correctness and immutability of voting results once finalized, to protect decision-making from fraudulent or erroneous alterations.
-We annotate each property explicitly using Scribble, enabling Mythril to systematically verify these essential conditions.
-
-Once the properties are specified, we recompile the smart contract code using Scribble, then analyze it using Mythril’s symbolic execution engine.
-Mythril traverses possible execution paths, trying to invalidate the assertions that were defined earlier.
-If any violation is discovered by Mythril, it returns a counterexample and a symbolic execution path that led to the issue.
-
-Upon encountering counterexamples, we analyze whether these findings represent genuine logic flaws or overly restrictive specifications.
-If there is a genuine logic flaw, we will flag it for review, while the latter will cause us to refine our annotations.
-We will evaluate the performance of our verification framework by testing it on both authentic DAO contracts and synthetic contracts that are injected with known vulnerabilities.
-Our goal is to produce a streamlined workflow that runs lightweight yet rigorous annotation-driven formal verification to ensure that Ethereum-based DAO governance contracts are secure.
-
-We will first test synthetically vulnerable smart contracts specifically designed to contain known security flaws related to DAO voting.
-This initial step allows us to validate the correctness of our verification techniques in detecting deliberate vulnerabilities.
-After establishing confidence in our methodology, we will progress to analyzing a realistic and manageable contract such as MolochDAO v2[14], to test our verification framework in a practical but simplified real-world scenario.
-
-We began by successfully setting up Mythril and integrating Scribble annotations for formal verification.
-To validate our setup, we created a simplified DAO smart contract example, incorporating core DAO functionalities.
-We annotated the critical sections using Scribble to define security properties explicitly.
-Running Mythril against this annotated DAO allowed us to verify that our environment and workflow operate correctly, establishing a solid foundation for further verification of more complex real-world DAOs.
-
-\section{Implementation}
-To be written
-
-\section{Evaluation}
-
-This project investigates whether symbolic execution can be used to verify the safety and liveness properties of DAO voting functions.
-It also explores the scalability of this approach when applied to more complex voting mechanisms and assesses whether the method can be adapted to different DAOs' smart contracts.
-If automation isn't feasible, we want to investigate the manual effort required for adaptation.
-Our experiments will involve both toy examples and open-source smart contracts, focusing on analyzing DAO voting logic and defining the properties needed to verify it.
-
-\section{Conclusion}
-To be written
-
-\section{Who Did What}
-\begin{itemize}
-    \item Aidan: Contributed to the Introduction, Threat Model, and References
-    \item Anish: Contributed to the Approach, Set up repository, dependencies, and starter DAO contract/annotations
-    \item Jeffrey: Contributed to the Background, State of the Art, and Evaluation sections
-\end{itemize}
-
-\begin{thebibliography}{00}
-\bibitem{b1} J.
-Feist, G.
-Grieco, and A.
-Groce, “Slither: A static analysis framework for smart contracts,” 2019, pp.
-8–15.
-doi: https://doi.org/10.1109/WETSEB.2019.00008.
-Available: \url{https://ieeexplore.ieee.org/abstract/document/8823898?casa_token=SNthQs5W2d0AAAAA:XwX332JMCkj3hw8XZd9nKBxe2bKJZ3v3yUNJ3jPtangZ3L2nISxh_rbY8fBW2zXkaWa0QnqgqVE}
-\bibitem{b2} Z. Nehaï, P.-Y. Piriou, and F. Daumas, “Model-checking of smart contracts,” 2018, pp. 980–987. Available: \url{https://ieeexplore.ieee.org/abstract/document/8726806}
-\bibitem{b3} J.
-He, M.
-Balunović, N.
-Ambroladze, P.
-Tsankov, and M.
-Vechev, “Learning to Fuzz from Symbolic Execution with Application to Smart Contracts,” Proceedings of the 2019 ACM SIGSAC Conference on Computer and Communications Security, pp.
-531–548, Nov.
-2019, Available: \url{https://dl.acm.org/doi/abs/10.1145/3319535.3363230?casa_token=5cBcZneJt7oAAAAA:sPluGu-gtO_db3qLqHUcylo4ksy4Rx0FBkiEBFom7You4VltkgLyZanIwgg-WHfLDVmrwmU0MbdpGA}
-\bibitem{b4} N. Sharma and S. Sharma, “A Survey of Mythril, A Smart Contract Security Analysis Tool for EVM Bytecode,” Indian Journal of Natural Sciences, vol. 12, no. 75, Dec. 2022, Available:
-\url{https://www.researchgate.net/profile/Swati-Sharma-171/publication/366391033_A_Survey_of_Mythril_A_Smart_Contract_Security_Analysis_Tool_for_EVM_Bytecode/links/639ecbdc095a6a77743c8073/A-Survey-of-Mythril-A-Smart-Contract-Security-Analysis-Tool-for-EVM-Bytecode.pdf}
-\bibitem{b5} ConsenSysDiligence, “GitHub - ConsenSysDiligence/scribble: Scribble instrumentation tool,” GitHub, Apr. 09, 2025. Available:  
-\url{ConsenSysDiligence, “GitHub - ConsenSysDiligence/scribble: Scribble instrumentation tool,” GitHub, Apr.
-09, 2025.
-https://github.com/ConsenSysDiligence/scribble/tree/develop (accessed Apr.
-10, 2025).}
-\bibitem{6} S. Nakamoto, “Bitcoin: a Peer-to-Peer Electronic Cash System,” bitcoin.org, Oct. 2008. Available: 
-\url{https://bitcoin.org/bitcoin.pdf}
-\bibitem{7} V. Buterin, “Ethereum Whitepaper,” Ethereum, 2014. Available: 
-\url{https://ethereum.org/en/whitepaper/}
-\bibitem{8} P. Wackerow, “Introduction to smart contracts,” ethereum.org, Sep. 02, 2022. Available: 
-\url{https://ethereum.org/en/developers/docs/smart-contracts/}
-\bibitem{9} N. Szabo, “Smart Contracts,” www.fon.hum.uva.nl, 1994. 
-\url{https://www.fon.hum.uva.nl/rob/Courses/InformationInSpeech/CDROM/Literature/LOTwinterschool2006/szabo.best.vwh.net/smart.contracts.html}
-\bibitem{10} C. Jentzsch, “DECENTRALIZED AUTONOMOUS ORGANIZATION TO AUTOMATE GOVERNANCE,” 2016. Available: 
-\url{https://lawofthelevel.lexblogplatformthree.com/wp-content/uploads/sites/187/2017/07/WhitePaper-1.pdf}
-\bibitem{11} C. Shier et al., “Understanding a Revolutionary and Flawed Grand Experiment in Blockchain: The DAO Attack,” SSRN Electronic Journal, 2017, doi: 
-\url{https://doi.org/10.2139/ssrn.3014782.}
-\bibitem{12} “List of 41 DAOs (2025),” Alchemy, 2025. Available:
-\url{https://www.alchemy.com/dapps/top/daos}
-\bibitem{13} K. Nekrasov, “DAO Voting Vulnerabilities,” Mixbytes.io, 2024.
-\url{https://mixbytes.io/blog/dao-voting-vulnerabilities}
-\bibitem{14} HausDAO, “GitHub - HausDAO/Molochv2.1: Moloch DAO v2 with multi-summoner capabilities, plus register function for metadata.,” GitHub, 2020. Available:
-\url{https://github.com/HausDAO/Molochv2.1}
-\end{thebibliography}
-\end{document}

### 2025-04-27 paper.tex
Layout final paper

@@
 \maketitle
+
+\section{Abstract}
+To be written
 
@@
 
-\section{Approach}
-Our approach uses Scribble and Mythril together to formally verify critical correctness properties in Ethereum-based DAO voting contracts.
-To begin, we identify essential governance rules found in most DAO implementations and articulate them into specific safety and liveness properties.
-Some key requirements include only token holders being able to vote, as well as prevention of double counting votes.
-These rules are expressed through Scribble annotations, which convert informal governance assumptions into precise assertions that are embedded into the Solidity contract.
-
-Our verification approach targets three core properties critical to DAO smart contract security.
-First, we verify Single Vote Enforcement, confirming that each member is restricted to casting only one vote per proposal, preventing potential manipulation through multiple votes.
-Second, we ensure Authorized Access, validating that voting and proposal functionalities are limited exclusively to authorized DAO members, thus safeguarding against unauthorized interference.
-Lastly, we confirm Integrity of Proposal Outcome, ensuring the correctness and immutability of voting results once finalized, to protect decision-making from fraudulent or erroneous alterations.
-We annotate each property explicitly using Scribble, enabling Mythril to systematically verify these essential conditions.
-
-Once the properties are specified, we recompile the smart contract code using Scribble, then analyze it using Mythril’s symbolic execution engine.
-Mythril traverses possible execution paths, trying to invalidate the assertions that were defined earlier.
-If any violation is discovered by Mythril, it returns a counterexample and a symbolic execution path that led to the issue.
-
-Upon encountering counterexamples, we analyze whether these findings represent genuine logic flaws or overly restrictive specifications.
-If there is a genuine logic flaw, we will flag it for review, while the latter will cause us to refine our annotations.
-We will evaluate the performance of our verification framework by testing it on both authentic DAO contracts and synthetic contracts that are injected with known vulnerabilities.
-Our goal is to produce a streamlined workflow that runs lightweight yet rigorous annotation-driven formal verification to ensure that Ethereum-based DAO governance contracts are secure.
-
-We will first test synthetically vulnerable smart contracts specifically designed to contain known security flaws related to DAO voting.
-This initial step allows us to validate the correctness of our verification techniques in detecting deliberate vulnerabilities.
-After establishing confidence in our methodology, we will progress to analyzing a realistic and manageable contract such as MolochDAO v2[14], to test our verification framework in a practical but simplified real-world scenario.
-
-We began by successfully setting up Mythril and integrating Scribble annotations for formal verification.
-To validate our setup, we created a simplified DAO smart contract example, incorporating core DAO functionalities.
-We annotated the critical sections using Scribble to define security properties explicitly.
-Running Mythril against this annotated DAO allowed us to verify that our environment and workflow operate correctly, establishing a solid foundation for further verification of more complex real-world DAOs.
+\section{Implementation}
+To be written
 
@@
 
-\section{Plan of Work}
-We have already begun by studying the relevant tools, Scribble and Mythril, in order to understand the specification language and the way Mythril verifies security properties after they have been defined by Scribble.
-Next, we wrote a simple DAO contract, defined a security property in Slither, and verified the property using Mythril as an end-to-end test of our research procedure.
-We will go on to define security properties for each voting vulnerability in each smart contract that we plan to test.
-Over the next week we will verify the first three DAO contracts in our suite, and then in the final week we will verify the last two along with our final write-up.
-Our expected goal is to verify three different security properties in these five contracts.
-Our stretch goal would be to verify these properties in 10 contracts, but at minimum we expect to fully verify these properties in three contracts from our test suite.
+\section{Conclusion}
+To be written
 

### 2025-04-27 paper.tex
Design section

--- 2025-04-27 paper.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
-\usepackage{url}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{xcolor}
-\usepackage{tikz}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Formally Verifying Voter Security Properties in DAO Smart Contracts}
-
-\author{
-    \makebox[\textwidth][c]{%
-        \begin{minipage}{0.45\textwidth}
-            \centering
-            \textbf{Anish Toomu} \\
-            \textit{Department of Computer Science} \\
-            \textit{University of North Carolina at Chapel Hill} \\
-            Chapel Hill, North Carolina, USA
-        \end{minipage}
-        \hfill
-        \begin{minipage}{0.45\textwidth}
-            \centering
-            \textbf{Aidan Maguire} \\
-            \textit{Department of Computer Science} \\
-            \textit{University of North Carolina at Chapel Hill} \\
-            Chapel Hill, North Carolina, USA
-        \end{minipage}
-    }\\[1.5em]
-
-    \makebox[\textwidth][c]{%
-        \begin{minipage}{0.6\textwidth}
-            \centering
-            \textbf{Jeffrey Zhang} \\
-            \textit{Department of Computer Science} \\
-            \textit{University of North Carolina at Chapel Hill} \\
-            Chapel Hill, North Carolina, USA
-        \end{minipage}
-    }
-}
-
-\maketitle
-
-\section{Introduction}
-This project aims to make use of two existing security tools to define and verify security properties for voting methods across a suite of Ethereum blockchain programs.
-Many Ethereum blockchain programs take the form of a DAO, or Decentralized Autonomous Organization, wherein users holding tokens that verify them as members of the organization can spend those tokens to vote on decision-making for the DAO as a whole.
-There are several types of vulnerabilities that have been identified in these types of contracts, but for this paper we will be looking at vulnerabilities surrounding the vote system that allow attackers to exploit the democratic principles behind DAOs.
-
-Our proposal intends to formally verify a suite of the most used DAO contracts to confirm that they are secure.
-We will require the use of Scribble, a specification language that allows us to define security properties for DAO contracts as annotations within the contracts themselves.
-We will then use Mythril, a security-analysis tool, to verify each of our newly defined security properties for our suite of popular contracts.
-If successful, we will increase the confidence in these widely-used contracts.
-Possible challenges include the properties not being entirely specifiable in Scribble's specification language, and some contracts being too complex to analyze with Mythril due to state explosion.
-
-\section{State of the Art}
-
-DAOs are a type of smart contract that define the rules and structure of a organization.
-In more general terms, DAOs represent decentralized communities that can allocate resources without centralized leadership.
-While there exist tools for various methods of verifying and bug-finding in smart contracts including static analysis[1], model checking[2], and symbolic execution[3], they haven’t been narrowed down to focus on DAOs, and the specific exploits that come with their voting systems, a key, shared property across DAOs and a critical part of their operations.
-We have chosen to use an existing symbolic execution-based tool, Mythril[4], along with Scribble[5], a specification language for properties in this work.
-
-\section{Background}
-To understand our proposed enhancements to Mythril, we must first grasp the fundamental concepts of the blockchain, the Ethereum blockchain and its innovative smart contracts, and finally DAOs, a subset of smart contracts with common functionalities.
-
-\subsection{Blockchain}
-A blockchain serves as a ledger of transactions that is transparent, decentralized, and secure.
-Each block in the chain contains information about transactions allowing anyone to inspect them at any time.
-Additionally, each block contains a cryptographic hash of the previous block in the chain.
-This chain means that in the event of a block being tampered with by an attacker, all of the altered blocks' successors would also be changed.
-The consensus needed to accept a chain also provides further security.
-If the majority of the computational power on the network is controlled by honest parties then the honest chain will be accepted.
-An attacker seeking to change a block would need to alter the block, redo all the proof-of-work computation for it and its successor blocks, and then catch up to the honest chain to be accepted.
-This proves to be computationally infeasible[6].
-
-\subsection{Ethereum and Smart Contracts}
-Ethereum, as proposed by Vitalik Buterin in 2014, seeks to provide an alternative to Bitcoin with a focus on the development of decentralized applications.
-This is achieved through a blockchain that contains a built-in Turing-complete language[7].
-This language allows users to write smart contracts that are stored on the blockchain.
-Smart contracts are a type of account, they have a balance and can be interacted with through transactions.
-They differ from users’ externally owned accounts in their method of control.
-Where externally owned accounts are controlled by user decisions, smart contracts are programs that run on the blockchain according to their code.
-Users or other smart contracts interact with smart contracts by sending a transaction that executes the functions defined by the contract’s code.
-Smart contracts automatically execute when their conditions are met, are universally visible, and are unable to be changed once uploaded[8].
-In this way smart contracts provide a trustworthy, automated way to enforce agreements, reducing the need for third-party enforcement, minimizing exceptions, and lowering the risk of fraud[9].
-
-\subsection{Decentralized Autonomous Organizations}
-Decentralized Autonomous Organizations (DAOs) use the blockchain and smart contracts as a way to govern and operate an organization without a central authority.
-DAOs allow participants to vote on proposed policy changes, actions taken by the organization, and any number of other decisions.
-These rules are automatically enforced by smart contracts.
-The first notable DAO, “The DAO” was formed on the Ethereum blockchain in 2016 as a venture capital fund.
-Users could exchange ether for tokens that gave holders voting power in The DAO proportional to the amount of tokens owned[10].
-The organization managed to crowdfund \$168M worth of ether representing one of the largest projects on the Ethereum blockchain.
-The project is now synonymous with a programming vulnerability in the organization's smart contract that allowed an attacker to siphon off \$50M from The DAO’s[11] gathered funds.
-This resulted in the controversial hard fork of the Ethereum blockchain and the shuttering of the organization.
-This example highlights the critical nature of DAO smart contract security as they manage large amounts of currency and interact with a large number of users.
-Today, a great variety of DAOs exist on Ethereum ranging from communities of creators to venture capital groups[12].
-
-\section{Threat Model}
-DAO contract voting vulnerabilities refers to a class of vulnerabilities where an attacker exploits the contract voting mechanism to vote twice with the same tokens, remove other people's votes, vote on a proposal and immediately put it into effect without giving other token holders a chance to vote themselves, or other similar exploits that undermine the decentralized democratic goals of DAO contracts.
-In our analysis, we assume that attackers have complete visibility of the contract code, and the ability to deploy their own contracts to the blockchain that interface with DAO contracts[13]; however, we are assuming that attackers cannot launch larger Ethereum network attacks such as network congestion or miner manipulation that would require greater coordination and resources.
-We consider nonvoting-related attacks such as integer overflow, reentrancy, and gas DoS attacks as out of scope for this paper.
-
-\section{Design}
-\subsection{Defining security properties for DAO smart contracts}
-\begin{center}
-\begin{tikzpicture}[scale=0.15]
-\tikzstyle{every node}+=[inner sep=0pt]
-\draw [black] (9,-32.6) circle (3);
-\draw (9,-32.6) node {$s_1,s_2$};
-\draw [black] (23.6,-16) circle (3);
-\draw (23.6,-16) node {$D_1$};
-\draw [black] (23.6,-49.3) circle (3);
-\draw (23.6,-49.3) node {$W_1$};
-\draw [black] (42.4,-16) circle (3);
-\draw (42.4,-16) node {$D_2$};
-\draw [black] (57.2,-16) circle (3);
-\draw (57.2,-16) node {$D_3$};
-\draw [black] (43.6,-49.3) circle (3);
-\draw (43.6,-49.3) node {$W_2$};
-\draw [black] (57.2,-49.3) circle (3);
-\draw (57.2,-49.3) node {$W_3$};
-\draw [black] (46.4,-32.6) circle (3);
-\draw (46.4,-32.6) node {$I$};
-\draw [black] (28.7,-32.6) circle (3);
-\draw (28.7,-32.6) node {$R$};
-\draw [black] (10.98,-30.35) -- (21.62,-18.25);
-\fill [black] (21.62,-18.25) -- (20.71,-18.52) -- (21.47,-19.18);
-\draw (16.84,-25.75) node [right] {$a_1$};
-\draw [black] (10.97,-34.86) -- (21.63,-47.04);
-\fill [black] (21.63,-47.04) -- (21.48,-46.11) -- (20.72,-46.77);
-\draw (16.84,-39.5) node [right] {$a_2$};
-\draw [black] (26.6,-16) -- (39.4,-16);
-\fill [black] (39.4,-16) -- (38.6,-15.5) -- (38.6,-16.5);
-\draw (33,-16.5) node [below] {$c_1$};
-\draw [black] (45.4,-16) -- (54.2,-16);
-\fill [black] (54.2,-16) -- (53.4,-15.5) -- (53.4,-16.5);
-\draw (49.8,-16.5) node [below] {$d_1$};
-\draw [black] (26.6,-49.3) -- (40.6,-49.3);
-\fill [black] (40.6,-49.3) -- (39.8,-48.8) -- (39.8,-49.8);
-\draw (33.6,-49.8) node [below] {$c_2$};
-\draw [black] (46.6,-49.3) -- (54.2,-49.3);
-\fill [black] (54.2,-49.3) -- (53.4,-48.8) -- (53.4,-49.8);
-\draw (50.4,-49.8) node [below] {$d_2$};
-\draw [black] (8.934,-29.602) arc (-182.00565:-319.9871:26.325);
-\fill [black] (8.93,-29.6) -- (9.46,-28.82) -- (8.46,-28.79);
-\draw [black] (55.065,-51.406) arc (-48.49526:-169.72438:27.748);
-\fill [black] (9.37,-35.58) -- (9.03,-36.45) -- (10.01,-36.27);
-\draw [black] (43.4,-32.6) -- (31.7,-32.6);
-\fill [black] (31.7,-32.6) -- (32.5,-33.1) -- (32.5,-32.1);
-\draw (37.55,-33.1) node [below] {$f$};
-\draw [black] (24.48,-18.87) -- (27.82,-29.73);
-\fill [black] (27.82,-29.73) -- (28.06,-28.82) -- (27.11,-29.11);
-\draw (25.38,-24.93) node [left] {$b_1$};
-\draw [black] (24.48,-46.43) -- (27.82,-35.47);
-\fill [black] (27.82,-35.47) -- (27.11,-36.09) -- (28.07,-36.38);
-\draw (26.92,-41.57) node [right] {$b_2$};
-\draw [black] (43.1,-18.92) -- (45.7,-29.68);
-\fill [black] (45.7,-29.68) -- (46,-28.79) -- (45.02,-29.02);
-\draw (43.64,-24.73) node [left] {$e_1$};
-\draw [black] (44.1,-46.34) -- (45.9,-35.56);
-\fill [black] (45.9,-35.56) -- (45.28,-36.27) -- (46.26,-36.43);
-\draw (45.71,-41.18) node [right] {$e_2$};
-\end{tikzpicture}
-\end{center}
-
-\section{Approach}
-Our approach uses Scribble and Mythril together to formally verify critical correctness properties in Ethereum-based DAO voting contracts.
-To begin, we identify essential governance rules found in most DAO implementations and articulate them into specific safety and liveness properties.
-Some key requirements include only token holders being able to vote, as well as prevention of double counting votes.
-These rules are expressed through Scribble annotations, which convert informal governance assumptions into precise assertions that are embedded into the Solidity contract.
-
-Our verification approach targets three core properties critical to DAO smart contract security.
-First, we verify Single Vote Enforcement, confirming that each member is restricted to casting only one vote per proposal, preventing potential manipulation through multiple votes.
-Second, we ensure Authorized Access, validating that voting and proposal functionalities are limited exclusively to authorized DAO members, thus safeguarding against unauthorized interference.
-Lastly, we confirm Integrity of Proposal Outcome, ensuring the correctness and immutability of voting results once finalized, to protect decision-making from fraudulent or erroneous alterations.
-We annotate each property explicitly using Scribble, enabling Mythril to systematically verify these essential conditions.
-
-Once the properties are specified, we recompile the smart contract code using Scribble, then analyze it using Mythril’s symbolic execution engine.
-Mythril traverses possible execution paths, trying to invalidate the assertions that were defined earlier.
-If any violation is discovered by Mythril, it returns a counterexample and a symbolic execution path that led to the issue.
-
-Upon encountering counterexamples, we analyze whether these findings represent genuine logic flaws or overly restrictive specifications.
-If there is a genuine logic flaw, we will flag it for review, while the latter will cause us to refine our annotations.
-We will evaluate the performance of our verification framework by testing it on both authentic DAO contracts and synthetic contracts that are injected with known vulnerabilities.
-Our goal is to produce a streamlined workflow that runs lightweight yet rigorous annotation-driven formal verification to ensure that Ethereum-based DAO governance contracts are secure.
-
-We will first test synthetically vulnerable smart contracts specifically designed to contain known security flaws related to DAO voting.
-This initial step allows us to validate the correctness of our verification techniques in detecting deliberate vulnerabilities.
-After establishing confidence in our methodology, we will progress to analyzing a realistic and manageable contract such as MolochDAO v2[14], to test our verification framework in a practical but simplified real-world scenario.
-
-We began by successfully setting up Mythril and integrating Scribble annotations for formal verification.
-To validate our setup, we created a simplified DAO smart contract example, incorporating core DAO functionalities.
-We annotated the critical sections using Scribble to define security properties explicitly.
-Running Mythril against this annotated DAO allowed us to verify that our environment and workflow operate correctly, establishing a solid foundation for further verification of more complex real-world DAOs.
-
-\section{Evaluation}
-
-This project investigates whether symbolic execution can be used to verify the safety and liveness properties of DAO voting functions.
-It also explores the scalability of this approach when applied to more complex voting mechanisms and assesses whether the method can be adapted to different DAOs' smart contracts.
-If automation isn't feasible, we want to investigate the manual effort required for adaptation.
-Our experiments will involve both toy examples and open-source smart contracts, focusing on analyzing DAO voting logic and defining the properties needed to verify it.
-
-\section{Plan of Work}
-We have already begun by studying the relevant tools, Scribble and Mythril, in order to understand the specification language and the way Mythril verifies security properties after they have been defined by Scribble.
-Next, we wrote a simple DAO contract, defined a security property in Slither, and verified the property using Mythril as an end-to-end test of our research procedure.
-We will go on to define security properties for each voting vulnerability in each smart contract that we plan to test.
-Over the next week we will verify the first three DAO contracts in our suite, and then in the final week we will verify the last two along with our final write-up.
-Our expected goal is to verify three different security properties in these five contracts.
-Our stretch goal would be to verify these properties in 10 contracts, but at minimum we expect to fully verify these properties in three contracts from our test suite.
-
-\section{Who Did What}
-\begin{itemize}
-    \item Aidan: Contributed to the Introduction, Threat Model, and References
-    \item Anish: Contributed to the Approach, Set up repository, dependencies, and starter DAO contract/annotations
-    \item Jeffrey: Contributed to the Background, State of the Art, and Evaluation sections
-\end{itemize}
-
-\begin{thebibliography}{00}
-\bibitem{b1} J.
-Feist, G.
-Grieco, and A.
-Groce, “Slither: A static analysis framework for smart contracts,” 2019, pp.
-8–15.
-doi: https://doi.org/10.1109/WETSEB.2019.00008.
-Available: \url{https://ieeexplore.ieee.org/abstract/document/8823898?casa_token=SNthQs5W2d0AAAAA:XwX332JMCkj3hw8XZd9nKBxe2bKJZ3v3yUNJ3jPtangZ3L2nISxh_rbY8fBW2zXkaWa0QnqgqVE}
-\bibitem{b2} Z. Nehaï, P.-Y. Piriou, and F. Daumas, “Model-checking of smart contracts,” 2018, pp. 980–987. Available: \url{https://ieeexplore.ieee.org/abstract/document/8726806}
-\bibitem{b3} J.
-He, M.
-Balunović, N.
-Ambroladze, P.
-Tsankov, and M.
-Vechev, “Learning to Fuzz from Symbolic Execution with Application to Smart Contracts,” Proceedings of the 2019 ACM SIGSAC Conference on Computer and Communications Security, pp.
-531–548, Nov.
-2019, Available: \url{https://dl.acm.org/doi/abs/10.1145/3319535.3363230?casa_token=5cBcZneJt7oAAAAA:sPluGu-gtO_db3qLqHUcylo4ksy4Rx0FBkiEBFom7You4VltkgLyZanIwgg-WHfLDVmrwmU0MbdpGA}
-\bibitem{b4} N. Sharma and S. Sharma, “A Survey of Mythril, A Smart Contract Security Analysis Tool for EVM Bytecode,” Indian Journal of Natural Sciences, vol. 12, no. 75, Dec. 2022, Available:
-\url{https://www.researchgate.net/profile/Swati-Sharma-171/publication/366391033_A_Survey_of_Mythril_A_Smart_Contract_Security_Analysis_Tool_for_EVM_Bytecode/links/639ecbdc095a6a77743c8073/A-Survey-of-Mythril-A-Smart-Contract-Security-Analysis-Tool-for-EVM-Bytecode.pdf}
-\bibitem{b5} ConsenSysDiligence, “GitHub - ConsenSysDiligence/scribble: Scribble instrumentation tool,” GitHub, Apr. 09, 2025. Available:  
-\url{ConsenSysDiligence, “GitHub - ConsenSysDiligence/scribble: Scribble instrumentation tool,” GitHub, Apr.
-09, 2025.
-https://github.com/ConsenSysDiligence/scribble/tree/develop (accessed Apr.
-10, 2025).}
-\bibitem{6} S. Nakamoto, “Bitcoin: a Peer-to-Peer Electronic Cash System,” bitcoin.org, Oct. 2008. Available: 
-\url{https://bitcoin.org/bitcoin.pdf}
-\bibitem{7} V. Buterin, “Ethereum Whitepaper,” Ethereum, 2014. Available: 
-\url{https://ethereum.org/en/whitepaper/}
-\bibitem{8} P. Wackerow, “Introduction to smart contracts,” ethereum.org, Sep. 02, 2022. Available: 
-\url{https://ethereum.org/en/developers/docs/smart-contracts/}
-\bibitem{9} N. Szabo, “Smart Contracts,” www.fon.hum.uva.nl, 1994. 
-\url{https://www.fon.hum.uva.nl/rob/Courses/InformationInSpeech/CDROM/Literature/LOTwinterschool2006/szabo.best.vwh.net/smart.contracts.html}
-\bibitem{10} C. Jentzsch, “DECENTRALIZED AUTONOMOUS ORGANIZATION TO AUTOMATE GOVERNANCE,” 2016. Available: 
-\url{https://lawofthelevel.lexblogplatformthree.com/wp-content/uploads/sites/187/2017/07/WhitePaper-1.pdf}
-\bibitem{11} C. Shier et al., “Understanding a Revolutionary and Flawed Grand Experiment in Blockchain: The DAO Attack,” SSRN Electronic Journal, 2017, doi: 
-\url{https://doi.org/10.2139/ssrn.3014782.}
-\bibitem{12} “List of 41 DAOs (2025),” Alchemy, 2025. Available:
-\url{https://www.alchemy.com/dapps/top/daos}
-\bibitem{13} K. Nekrasov, “DAO Voting Vulnerabilities,” Mixbytes.io, 2024.
-\url{https://mixbytes.io/blog/dao-voting-vulnerabilities}
-\bibitem{14} HausDAO, “GitHub - HausDAO/Molochv2.1: Moloch DAO v2 with multi-summoner capabilities, plus register function for metadata.,” GitHub, 2020. Available:
-\url{https://github.com/HausDAO/Molochv2.1}
-\end{thebibliography}
-\end{document}
 \documentclass[conference]{IEEEtran}

### 2025-04-27 paper.tex
design section finished

@@
 We define the set $Q$ as follows:
+\begin{figure}[h]
+\caption{\textbf{The set $Q$}}
 \begin{center}
@@
 \end{center}
+\end{figure}
 
 And define the set $Sigma$ as follows:
+\begin{figure}[h]
+\caption{\textbf{The set $\Sigma$}}
 \begin{center}
@@
 \hline
-Vote function called & Member makes request to contract\\
+Function called & Member makes request to contract\\
 \hline
@@
 \end{center}
+\end{figure}
 
-And finally provide a diagram of the finite state machine.
+And finally provide a diagram of the finite state machine for the transition function (Figure 1). Terminating states are indicated with double rings.
+\begin{figure}[h]
 \begin{center}
@@
 \end{center}
+\caption{DAO Voting contract Finite State Machine}
+\end{figure}
 
@@
 \subsection{Security Properties for Secure DAO Voting}
+We define three properties for a secure DAO voting system:
+\begin{enumerate}
+    \item Singular Vote: A single member of the DAO should not be able to vote more than once, or have their vote count for more than one vote.
+    \item Vote Authorization: Anyone can make a vote request using the contract, but only DAO members (holders of the particular DAO token) should be able to vote.
+    \item Vote Finality: Once the interaction between the member and the DAO contract is finished, the vote count should not revert or otherwise be changed by the actions of another member.
+\end{enumerate}
 
-\section{Approach}
-Our approach uses Scribble and Mythril together to formally verify critical correctness properties in Ethereum-based DAO voting contracts.
-To begin, we identify essential governance rules found in most DAO implementations and articulate them into specific safety and liveness properties.
-Some key requirements include only token holders being able to vote, as well as prevention of double counting votes.
-These rules are expressed through Scribble annotations, which convert informal governance assumptions into precise assertions that are embedded into the Solidity contract.
-
-Our verification approach targets three core properties critical to DAO smart contract security.
-First, we verify Single Vote Enforcement, confirming that each member is restricted to casting only one vote per proposal, preventing potential manipulation through multiple votes.
-Second, we ensure Authorized Access, validating that voting and proposal functionalities are limited exclusively to authorized DAO members, thus safeguarding against unauthorized interference.
-Lastly, we confirm Integrity of Proposal Outcome, ensuring the correctness and immutability of voting results once finalized, to protect decision-making from fraudulent or erroneous alterations.
-We annotate each property explicitly using Scribble, enabling Mythril to systematically verify these essential conditions.
-
-Once the properties are specified, we recompile the smart contract code using Scribble, then analyze it using Mythril’s symbolic execution engine.
-Mythril traverses possible execution paths, trying to invalidate the assertions that were defined earlier.
-If any violation is discovered by Mythril, it returns a counterexample and a symbolic execution path that led to the issue.
-
-Upon encountering counterexamples, we analyze whether these findings represent genuine logic flaws or overly restrictive specifications.
-If there is a genuine logic flaw, we will flag it for review, while the latter will cause us to refine our annotations.
-We will evaluate the performance of our verification framework by testing it on both authentic DAO contracts and synthetic contracts that are injected with known vulnerabilities.
-Our goal is to produce a streamlined workflow that runs lightweight yet rigorous annotation-driven formal verification to ensure that Ethereum-based DAO governance contracts are secure.
-
-We will first test synthetically vulnerable smart contracts specifically designed to contain known security flaws related to DAO voting.
-This initial step allows us to validate the correctness of our verification techniques in detecting deliberate vulnerabilities.
-After establishing confidence in our methodology, we will progress to analyzing a realistic and manageable contract such as MolochDAO v2[14], to test our verification framework in a practical but simplified real-world scenario.
-
-We began by successfully setting up Mythril and integrating Scribble annotations for formal verification.
-To validate our setup, we created a simplified DAO smart contract example, incorporating core DAO functionalities.
-We annotated the critical sections using Scribble to define security properties explicitly.
-Running Mythril against this annotated DAO allowed us to verify that our environment and workflow operate correctly, establishing a solid foundation for further verification of more complex real-world DAOs.
+Properties 1 and 2 are collectively bundled as part of the \textit{Vote Validated} DAO contract event.
+Property 3 is covered in our model by the terminating path of execution and lack of looping.
+Each call of the vote function is treated as a separate execution.
 

### 2025-04-28 hardhat.config.js
simple tests

@@ -1,24 +1,0 @@
-require("@nomicfoundation/hardhat-toolbox");
-require("@nomicfoundation/hardhat-ethers");
-
-/** @type import('hardhat/config').HardhatUserConfig */
-module.exports = {
-  solidity: {
-    version: "0.8.29",
-    settings: {
-      optimizer: {
-        enabled: true,
-        runs: 200
-      }
-    }
-  },
-  paths: {
-    sources: "./contracts",
-    tests: "./test",
-    cache: "./cache",
-    artifacts: "./artifacts"
-  },
-  mocha: {
-    timeout: 40000
-  }
-}; 

### 2025-04-28 hardhat.config.ts

@@ -1,13 +1,0 @@
-import { HardhatUserConfig } from "hardhat/config";
-import "@nomicfoundation/hardhat-toolbox";
-
-const config: HardhatUserConfig = {
-  solidity: "0.8.29",
-  networks: {
-    localhost: {
-      url: "http://127.0.0.1:8545"
-    }
-  }
-};
-
-export default config; 

### 2025-04-28 scripts/deploy.ts

@@ -1,14 +1,0 @@
-import { ethers } from "hardhat";
-
-async function main() {
-  const SimpleDAO = await ethers.getContractFactory("SimpleDAO");
-  const dao = await SimpleDAO.deploy();
-  await dao.waitForDeployment();
-
-  console.log("SimpleDAO deployed to:", await dao.getAddress());
-}
-
-main().catch((error) => {
-  console.error(error);
-  process.exitCode = 1;
-}); 

### 2025-04-28 scripts/run_analysis.js

@@ -1,73 +1,0 @@
-const { execSync } = require('child_process');
-const fs = require('fs');
-const path = require('path');
-
-// Configuration
-const CONFIG = {
-  scribbleConfig: path.join(__dirname, '../config/scribble.json'),
-  contractPath: path.join(__dirname, '../contracts/SimpleDAO.sol'),
-  instrumentedPath: path.join(__dirname, '../instrumented'),
-  testPath: path.join(__dirname, '../test/SimpleDAO.test.js'),
-};
-
-// Ensure directories exist
-function ensureDirectories() {
-  const dirs = [
-    path.dirname(CONFIG.scribbleConfig),
-    path.dirname(CONFIG.contractPath),
-    CONFIG.instrumentedPath,
-    path.dirname(CONFIG.testPath),
-  ];
-  
-  dirs.forEach(dir => {
-    if (!fs.existsSync(dir)) {
-      fs.mkdirSync(dir, { recursive: true });
-      console.log(`Created directory: ${dir}`);
-    }
-  });
-}
-
-// Run Scribble instrumentation
-function runScribble() {
-  console.log('Running Scribble instrumentation...');
-  try {
-    execSync(`npx scribble --output-mode files --utils-output-path ${CONFIG.instrumentedPath} ${CONFIG.contractPath}`, { stdio: 'inherit' });
-    console.log('Scribble instrumentation completed successfully.');
-  } catch (error) {
-    console.error('Error running Scribble instrumentation:', error.message);
-    process.exit(1);
-  }
-}
-
-// Run Hardhat tests
-function runTests() {
-  console.log('Running Hardhat tests...');
-  try {
-    execSync('npx hardhat test', { stdio: 'inherit' });
-    console.log('Hardhat tests completed successfully.');
-  } catch (error) {
-    console.error('Error running Hardhat tests:', error.message);
-    process.exit(1);
-  }
-}
-
-// Main function
-async function main() {
-  console.log('Starting SimpleDAO analysis...');
-  
-  // Ensure all directories exist
-  ensureDirectories();
-  
-  // Run Scribble instrumentation
-  runScribble();
-  
-  // Run Hardhat tests
-  runTests();
-  
-  console.log('SimpleDAO analysis completed successfully.');
-}
-
-main().catch(error => {
-  console.error('Error in main:', error);
-  process.exit(1);
-}); 

### 2025-04-28 scripts/run_mythril.py

@@ -1,63 +1,0 @@
-#!/usr/bin/env python3
-import os
-import subprocess
-import sys
-from pathlib import Path
-
-def run_mythril_analysis(contract_path):
-    """
-    Run Mythril analysis on a given contract file.
-    
-    Args:
-        contract_path (str): Path to the contract file to analyze
-    """
-    try:
-        # Run mythril analyze command
-        cmd = [
-            "myth",
-            "analyze",
-            contract_path,
-            "--execution-timeout", "60",  # 60 second timeout
-            "--max-depth", "3",  # Transaction depth
-            "--solver-timeout", "60000",  # 60 second solver timeout
-            "--pruning-factor", "0.8"  # Pruning factor for state space
-        ]
-        
-        print(f"Running Mythril analysis on {contract_path}...")
-        result = subprocess.run(cmd, capture_output=True, text=True)
-        
-        if result.returncode == 0:
-            print("Analysis completed successfully!")
-            print(result.stdout)
-        else:
-            print("Analysis found potential issues:")
-            print(result.stdout)
-            print("Errors/Warnings:")
-            print(result.stderr)
-            
-    except Exception as e:
-        print(f"Error running Mythril analysis: {str(e)}")
-        sys.exit(1)
-
-def main():
-    # Get the instrumented contracts directory
-    instrumented_dir = Path("instrumented")
-    contracts_dir = Path("contracts")
-    
-    if not instrumented_dir.exists():
-        print("Warning: instrumented directory not found. Checking contracts directory...")
-    
-    # Find all .sol files in both directories
-    sol_files = list(instrumented_dir.glob("**/*.sol")) + list(contracts_dir.glob("**/*.sol.instrumented"))
-    
-    if not sol_files:
-        print("No instrumented .sol files found in either the instrumented or contracts directory.")
-        sys.exit(1)
-    
-    # Run analysis on each contract
-    for contract in sol_files:
-        print(f"\nAnalyzing {contract}...")
-        run_mythril_analysis(str(contract))
-
-if __name__ == "__main__":
-    main() 

### 2025-04-29 paper.tex
new design

@@
 \begin{center}
-$M = (Q, \Sigma, \delta, q_0, F)$
+$M = (Q, \Sigma, \delta, q_0, F, u, p, v)$
 \end{center}
 
-With $Q$ being the set of contract states, $\Sigma$ being the set of events, $\delta$ being the transition function mapping $Q\times\Sigma$, $q_0$ being the initial state, and $F$ being the set of terminal states.
-We define the set $Q$ as follows:
+With $Q$ being the set of contract states, $\Sigma$ being the set of events, $\delta$ being the transition function mapping $Q\times\Sigma$, $q_0$ being the initial state, $F$ being the set of terminal states, $u$ being the user that is calling the DAO voting function (either manually or through another smart contract themselves), $p$ is the specific proposal being voted on, and $v$ is the intended vote of the user.
+All users $u$ have a unique DAO token balance $u_{balance}$ that is tracked by the contract.
+Additionally, we define $p_{user}$ as a function mapping of $P\times U$: for any given proposal and user, $p_{user}$ holds the current vote of that user.
+Given this function, we can also reason about a total vote count for each proposal defined as $p_{votes}$ as well as separate counts for each type of vote.
+For our model, we will only deal with two possible voting decisions, $p_{yes}$ and $p_{no}$, though actual implementations may allow DAO members more variation with the way they vote.
+
+We define the set of states $Q$ as follows:
 \begin{figure}[h]
@@
 
-And define the set $Sigma$ as follows:
+And define the set of events $Sigma$ as follows:
 \begin{figure}[h]
@@
 \subsection{Security Properties for Secure DAO Voting}
-We define three properties for a secure DAO voting system:
+We describe three basic properties for a secure DAO voting system:
 \begin{enumerate}
@@
     \item Vote Authorization: Anyone can make a vote request using the contract, but only DAO members (holders of the particular DAO token) should be able to vote.
-    \item Vote Finality: Once the interaction between the member and the DAO contract is finished, the vote count should not revert or otherwise be changed by the actions of another member.
+    \item Quorum Threshold: For a DAO proposal to be finalized, a minimum portion of the total eligible voters need to have voted.
+This prevents proposals from being enacted that only got a single yes vote, for example.
 \end{enumerate}
 
-Properties 1 and 2 are collectively bundled as part of the \textit{Vote Validated} DAO contract event.
-Property 3 is covered in our model by the terminating path of execution and lack of looping.
-Each call of the vote function is treated as a separate execution.
+We formalize these properties according to the $Vote\mbox{ }Validated$ event.
+For the $Vote\mbox{ }Validated$ event to trigger and to go from state $A$ to state $B$:
+\begin{center}
+$p_{user} = null \land u_{balance} > 0$. 
+\end{center}
+This ensures that potential voters are authorized members who have not already voted.
+We also need to define a second property to make sure that the proper behavior occurs when our contract terminates according to the current state of the FSM $q$ and previous state $q_{-1}$:
+\begin{center}
+    $q \in\{Y,N\}\xrightarrow{}p_{user} \neq null \land p_{votes} - q_{-1}$
+\end{center}
 
@@
 8–15.
-doi: https://doi.org/10.1109/WETSEB.2019.00008.
 Available: \url{https://ieeexplore.ieee.org/abstract/document/8823898?casa_token=SNthQs5W2d0AAAAA:XwX332JMCkj3hw8XZd9nKBxe2bKJZ3v3yUNJ3jPtangZ3L2nISxh_rbY8fBW2zXkaWa0QnqgqVE}

### 2025-04-29 paper.tex
Implementation

@@
 \usepackage{tikz}
+\usepackage{listings}
+\usepackage{xcolor}
+
+\lstset{
+  basicstyle=\ttfamily\small,
+  breaklines=true,
+  breakatwhitespace=true,
+  columns=fullflexible,
+  keepspaces=true,
+  frame=single,
+  numbers=none,
+  keywordstyle=\color{blue},
+  commentstyle=\color{gray},
+  language=, % <- no language syntax highlighting to prevent overflow issues
+}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \section{Implementation}
-To be written
+\subsection{Workflow}
+The basic voting security properties are applied to the selected smart contracts using the Scribble specification language.
+This takes the form of high-level annotations applied to the target functions in the smart contract code.
+These annotated files are then instrumented by Scribble to automatically generate Solidity code with the desired assertions and exceptions.
+The instrumented files are analyzed with Mythril to discover execution paths that violate the voting security properties.
+\subsection{Toy Examples}
+\begin{figure}[h]
+\centering
+\begin{lstlisting}[basicstyle=\ttfamily\small,breaklines=true]
+    // Flawed logic in not checking for previous votes
+
+    /// #if_succeeds {:msg "single-vote"} proposals[id].voted[msg.sender];
+
+    function vote(uint256 id, bool support) external {
+        require(isMember[msg.sender], "not a member");
+        Proposal storage p = proposals[id];
+
+        if (support) {
+            p.yes += 1;
+        } else {
+            p.no += 1;
+        }
+    }
+\end{lstlisting}
+\caption{Basic single vote flaw.}
+\label{fig:vote_function}
+\end{figure}
+
+\subsubsection{Singular Vote}
+
+\begin{figure}[h]
+\centering
+\begin{lstlisting}[basicstyle=\ttfamily\small,breaklines=true]
+    // Flawed logic in not checking for previous votes
+
+    /// #if_succeeds {:msg "single-vote"} proposals[id].voted[msg.sender];
+
+    function vote(uint256 id, bool support) external {
+        require(isMember[msg.sender], "not a member");
+        Proposal storage p = proposals[id];
+
+        if (support) {
+            p.yes += 1;
+        } else {
+            p.no += 1;
+        }
+    }
+\end{lstlisting}
+\caption{Basic single vote flaw.}
+\label{fig:vote_function}
+\end{figure}
 

### 2025-04-29 paper.tex
chenges

--- 2025-04-29 paper.tex
@@
 \usepackage{xcolor}
+\usepackage{listings}
 \usepackage{tikz}
+\lstset{
+  basicstyle=\ttfamily\small,
+  breaklines=true,
+  breakatwhitespace=true,
+  columns=fullflexible,
+  keepspaces=true,
+  frame=single,
+  numbers=none,
+  keywordstyle=\color{blue},
+  commentstyle=\color{gray},
+  language=, % <- no language syntax highlighting to prevent overflow issues
+}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 All DAOs have a voting function in their contract that allows members to vote on proposals made by other members.
-We represent the general form of this voting function as a finite state machine that DAO members can interact with.
+We represent the general form of this voting function as a finite state machine related to a given proposal $p \in P$, the set of all proposals in the DAO contract.
 We define the FSM as follows:
@@
 
-With $Q$ being the set of contract states, $\Sigma$ being the set of events, $\delta$ being the transition function mapping $Q\times\Sigma$, $q_0$ being the initial state, $F$ being the set of terminal states, $u$ being the user that is calling the DAO voting function (either manually or through another smart contract themselves), $p$ is the specific proposal being voted on, and $v$ is the intended vote of the user.
+With $Q$ being the set of voting function states, $\Sigma$ being the set of events triggering changes in state, $\delta$ being the transition function mapping $Q\times\Sigma$, $q_0$ being the initial state, $F$ being the set of terminal states, $u$ being the user that is calling the DAO voting function (either manually or through another smart contract themselves), $p$ is the specific proposal being voted on, and $v$ is the intended vote of the user.
 All users $u$ have a unique DAO token balance $u_{balance}$ that is tracked by the contract.
@@
 \hline
-$q_0$ & Initial state. Contract is inert.\\
+$q_0$ & Initial state. $u, v = null$\\
 \hline
-A & Vote request initiated. Voter identity set\\
+$q_1$ & $u, v$ are set based on vote request\\
 \hline
-B & Vote request validated\\
+$q_2$ & $p_{u} = null, u_{balance} > 0$\\
 \hline
-Y & Vote total updated in favor. Terminate interaction \\
+$Y$ & $p_{yes} += 1$ \\
 \hline
-N & Vote total updated against. Terminate interaction\\
+$N$ & $p_{no} += 1$\\
 \hline
-R & Vote canceled. Terminate interaction\\
+$R$ & $u = null$\\
+\hline
+$F$ & Proposal voting period ends\\
 \hline
@@
 \hline
+End & End transaction with user and return to initial state\\
+\hline
+Voting ends & Voting window for the proposal window closes\\
+\hline
 \end{tabular}
@@
 
-And finally provide a diagram of the finite state machine for the transition function (Figure 1). Terminating states are indicated with double rings.
+And finally provide a diagram of the finite state machine for the transition function (Figure 3). Terminating states are indicated with double rings.
 \begin{figure}[h]
 \begin{center}
-\begin{tikzpicture}[scale=0.2]
+\begin{tikzpicture}[scale=0.1705]
 \tikzstyle{every node}+=[inner sep=0pt]
@@
 \draw [black] (36.9,-22) circle (3);
-\draw (36.9,-22) node {$A$};
+\draw (36.9,-22) node {$q_1$};
 \draw [black] (36.9,-33.6) circle (3);
-\draw (36.9,-33.6) node {$B$};
+\draw (36.9,-33.6) node {$q_2$};
 \draw [black] (55.8,-22) circle (3);
 \draw (55.8,-22) node {$R$};
-\draw [black] (55.8,-22) circle (2.4);
-\draw [black] (45.7,-45.7) circle (3);
-\draw (45.7,-45.7) node {$N$};
-\draw [black] (45.7,-45.7) circle (2.4);
-\draw [black] (28.3,-45.7) circle (3);
-\draw (28.3,-45.7) node {$Y$};
-\draw [black] (28.3,-45.7) circle (2.4);
+\draw [black] (44.2,-41) circle (3);
+\draw (44.2,-41) node {$N$};
+\draw [black] (28.9,-41) circle (3);
+\draw (28.9,-41) node {$Y$};
+\draw [black] (36.9,-56.3) circle (3);
+\draw (36.9,-56.3) node {$F$};
+\draw [black] (36.9,-56.3) circle (2.4);
 \draw [black] (36.9,-12.6) -- (36.9,-19);
@@
 \draw (46.35,-22.5) node [below] {$Vote\mbox{ }rejected$};
-\draw [black] (38.66,-36.03) -- (43.94,-43.27);
-\fill [black] (43.94,-43.27) -- (43.87,-42.33) -- (43.06,-42.92);
-\draw (41.89,-38.27) node [right] {$Vote\mbox{ }no$};
-\draw [black] (35.16,-36.05) -- (30.04,-43.25);
-\fill [black] (30.04,-43.25) -- (30.91,-42.89) -- (30.09,-42.31);
-\draw (32.01,-38.28) node [left] {$Vote\mbox{ }yes$};
+\draw [black] (39.01,-35.74) -- (42.09,-38.86);
+\fill [black] (42.09,-38.86) -- (41.89,-37.94) -- (41.18,-38.65);
+\draw (41.08,-35.83) node [right] {$Vote\mbox{ }no$};
+\draw [black] (34.7,-35.64) -- (31.1,-38.96);
+\fill [black] (31.1,-38.96) -- (32.03,-38.79) -- (31.35,-38.05);
+\draw (28.99,-36.81) node [above] {$Vote\mbox{ }yes$};
+\draw [black] (53.29,-20.35) -- (39.41,-11.25);
+\fill [black] (39.41,-11.25) -- (39.8,-12.1) -- (40.35,-11.27);
+\draw (48.46,-15.3) node [above] {$End$};
+\draw [black] (25.96,-40.423) arc (-106.3473:-282.23982:16.379);
+\fill [black] (34.04,-8.7) -- (33.37,-8.04) -- (33.15,-9.02);
+\draw (13.94,-20.19) node [left] {$End$};
+\draw [black] (39.724,-8.599) arc (104.2931:-78.11737:16.458);
+\fill [black] (39.72,-8.6) -- (40.62,-8.89) -- (40.38,-7.92);
+\draw (60.57,-20.41) node [right] {$End$};
+\draw [black] (30.29,-43.66) -- (35.51,-53.64);
+\fill [black] (35.51,-53.64) -- (35.58,-52.7) -- (34.7,-53.16);
+\draw (32.22,-49.8) node [left] {$Voting\mbox{ }ends$};
+\draw [black] (42.91,-43.71) -- (38.19,-53.59);
+\fill [black] (38.19,-53.59) -- (38.99,-53.09) -- (38.09,-52.66);
+\draw (41.26,-49.71) node [right] {$Voting\mbox{ }ends$};
 \end{tikzpicture}
@@
 \end{figure}
+
+As stated above, this model represents the possible state space for the voting function of a given proposal.
 
@@
 This ensures that potential voters are authorized members who have not already voted.
-We also need to define a second property to make sure that the proper behavior occurs when our contract terminates according to the current state of the FSM $q$ and previous state $q_{-1}$:
+We also need to define a second property to make sure that the proper behavior occurs when our contract terminates according to the current state of the FSM $q$ and initial state $q_{0}$:
 \begin{center}
-    $q \in\{Y,N\}\xrightarrow{}p_{user} \neq null \land p_{votes} - q_{-1}$
+    $q \in\{Y,N\}\xrightarrow{}p_{user} \neq null \land p_{votes} - p_{votes}^0 = 1$
 \end{center}
 
+Where $p_{votes}^0$ is the value of $p_{votes}$ in the initial state of execution $q_0$. This ensures that votes are counted once and only once.
+
+The final security property, Quorum Threshold,
+
 \section{Implementation}
-To be written
+\subsection{Workflow}
 
+We started by defining our basic voting security properties in the DAOProperties.spec file.
+
+\begin{lstlisting}[basicstyle=\ttfamily\small,breaklines=true]
+    /// @title DAO Properties Specification
+    /// @notice Abstract properties that should hold for any DAO implementation
+
+    /// @property {:msg "Only token holders can vote"} 
+    ///     tokenBalances[msg.sender] > 0 || isMember[msg.sender] == true;
+
+    /// @property {:msg "Single vote per address"} 
+    ///     proposals[_proposalId].hasVoted[msg.sender] == true;
+
+    /// @property {:msg "Quorum is met before execution"} 
+    ///     (proposals[_proposalId].yesVotes + proposals[_proposalId].noVotes) >= 
+    ///     (totalTokens * QUORUM_THRESHOLD) / 100 || 
+    ///     proposals[_proposalId].numberOfVotes >= minimumQuorum;
+\end{lstlisting}
+
+We then manually annotated the target functions in the smart contract code with these properties.
+When we run Scribble on the annotated contract, it rewrites the Solidity source contract so that every property becomes a run-time assertion.
+We then feed this instrumented contract to Mythril, which symbolically explores all possible execution paths.
+If Mythril finds a path that violates one of our annotated conditions, it raises an AssertionFailed event with a corresponding message.
+
+Before we tried to annotate real world contracts, we built three deliberately flawed “toy” contracts: one for each vulnerability we were focusing on.
+This allowed us to tune our Scribble annotations on a simple contract with a much faster turnaround than having to wait hours for a complex contract to finish evaluating.
+
+The first toy contract (Figure 1) omits any check on a caller’s token balance, so non-holders can vote freely.
+The second (Figure 2) remembers votes in a mapping but never consults that mapping, allowing the same address to vote twice.
+The third (Figure 3) allows execution as soon as a “yes” majority exists, without verifying that the total number of votes meets the quorum threshold.
+
+\subsection{Toy Examples}
+
+\begin{figure}[h]
+\centering
+\begin{lstlisting}[basicstyle=\ttfamily\small,breaklines=true]
+    // Flawed logic: No token balance check
+
+    /// @property {:msg "Only token holders can vote"} 
+    ///     tokenBalances[msg.sender] > 0 || isMember[msg.sender] == true;
+
+    function vote(uint256 proposalId, bool support) external {
+        // Missing token balance check
+        Proposal storage p = proposals[proposalId];
+
+        if (support) {
+            p.yesVotes += 1;
+        } else {
+            p.noVotes += 1;
+        }
+        p.numberOfVotes += 1;
+    }
+\end{lstlisting}
+\caption{Authorization property: Only token holders can vote.}
+\label{fig:auth_property}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\begin{lstlisting}[basicstyle=\ttfamily\small,breaklines=true]
+    // Flawed logic: No check for previous votes
+
+    /// @property {:msg "Single vote per address"} 
+    ///     proposals[_proposalId].hasVoted[msg.sender] == true;
+
+    function vote(uint256 proposalId, bool support) external {
+        require(tokenBalances[msg.sender] > 0, "No tokens");
+        Proposal storage p = proposals[proposalId];
+
+        // Missing hasVoted check
+        if (support) {
+            p.yesVotes += 1;
+        } else {
+            p.noVotes += 1;
+        }
+        p.numberOfVotes += 1;
+    }
+\end{lstlisting}
+\caption{Single vote property: Each address can only vote once per proposal.}
+\label{fig:single_vote_property}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\begin{lstlisting}[basicstyle=\ttfamily\small,breaklines=true]
+    // Flawed logic: No quorum check before execution
+
+    /// @property {:msg "Quorum is met before execution"} 
+    ///     (proposals[_proposalId].yesVotes + proposals[_proposalId].noVotes) >= 
+    ///     (totalTokens * QUORUM_THRESHOLD) / 100 || 
+    ///     proposals[_proposalId].numberOfVotes >= minimumQuorum;
+
+    function executeProposal(uint256 proposalId) external {
+        Proposal storage p = proposals[proposalId];
+
+        // Missing quorum check
+        if (p.yesVotes > p.noVotes) {
+            // Execute proposal
+            p.executed = true;
+        }
+    }
+\end{lstlisting}
+\caption{Quorum property: Quorum must be met before execution.}
+\label{fig:quorum_property}
+\end{figure}
 \section{Evaluation}
+We evaluate 4 DAO smart contracts using the workflow outlined in Section VII. 
+\subsection{SimpleDAO} The first contract we examine is SimpleDAO.
+We create SimpleDAO as a basic DAO with token-weighted voting, quorum-dependent proposal execution, and self-contained code with no external calls.
+The Mythril symbolic execution analyzes the instrumented Solidity file finding no violation of the voting security properties.
+\subsection{FlawedDAO} The second example contract is FlawedDAO.
+This is a basic DAO contract that violates all of the voting security properties as a demonstration.
+The Mythril analysis of the contract results in the marking of all three violations.
+\subsection{dao-congress} The original specifications were designed for a token-based voting system, which we had to modify to accommodate the membership-based architecture of the Congress DAO implementation.
+For the authorization property, we replaced the token balance check with a membership verification, ensuring that only registered members (where memberId[msg.sender] != 0) can participate in voting.
+The single-vote-per-address property was implemented by verifying the state of the voted mapping after each vote transaction.
+Finally, the quorum requirement was adapted from a percentage-based token threshold to a simple vote count comparison against a minimum quorum value.
 
-This project investigates whether symbolic execution can be used to verify the safety and liveness properties of DAO voting functions.
-It also explores the scalability of this approach when applied to more complex voting mechanisms and assesses whether the method can be adapted to different DAOs' smart contracts.
-If automation isn't feasible, we want to investigate the manual effort required for adaptation.
-Our experiments will involve both toy examples and open-source smart contracts, focusing on analyzing DAO voting logic and defining the properties needed to verify it.
+\begin{figure}[h]
+\centering
+\begin{lstlisting}[basicstyle=\ttfamily\small,breaklines=true]
+SWC ID: 110
+Severity: Medium
+Contract: FlawedDAO
+Function name: finalize(uint256)
+PC address: 913
+Estimated Gas Usage: 16596 - 39024
+A user-provided assertion failed.
+--------------------
+In file: contracts/FlawedDAO.sol:123
+__ScribbleUtilsLib__373.AssertionFailed ("004763:0097:000 6: Quorum is met before execution")
+--------------------
+
+==== Exception State ====
+SWC ID: 110
+Severity: Medium
+Contract: FlawedDAO
+Function name: vote(uint256,bool)
+PC address: 1993
+Estimated Gas Usage: 13941 - 36039
+A user-provided assertion failed.
+--------------------
+In file: contracts/FlawedDAO.sol:94
+__ScribbleUtilsLib__373.AssertionFailed( "003414:0094:000 4: Only token holders can vote")
+--------------------
+==== Exception State ====
+SWC ID: 110
+Severity: Medium
+Contract: FlawedDAO
+Function name: vote(uint256,bool)
+PC address: 2157
+Estimated Gas Usage: 14962 - 37770
+A user-provided assertion failed.
+--------------------
+In file: contracts/FlawedDAO.sol:98
+__ScribbleUtilsLib__373.AssertionFailed ("003637:0090:000 5: Single vote per address")
+--------------------
+\end{lstlisting}
+\caption{Mythril output flagging property violations in \texttt{FlawedDAO}.}
+\label{fig:flawed_dao_assertions}
+\end{figure}
+
+\subsection{Association} The fourth contract we evaluate is Association CITE.
+This is an open-source DAO contract developed by the Ethereum Foundation.
+This contract represents a shareholder-controlled organization in which token holders vote on transactions that send funds to the proposed recipient.
+This contract is more complex than the previous examples, containing external calls to the \texttt{Token} interface and inheriting from two contracts.
+Mythril models external calls conservatively, assuming that the called function can result in any return.
+To accurately model the authorization property correctly, we create a hard-coded \texttt{mockBalanceOf} mapping locally that allows Mythril to reason about \texttt{sharesTokenAddress.balanceOf()} properly.
+For the quorum property, we add a helper function \texttt{hasQuorum()} to count the proposal's proportion of shares stored in an array of vote objects.
+This is done because Scribble does not provide functionality to loop and sum over an array.
+The greater complexity of the Association contract resulted in a state space explosion; unbounded symbolic execution of the contract led to segmentation faults and run times exceeding an hour.
+To counteract this, we tested the properties separately with bounded depth and runtime.
+During these bounded analyses, all three voting security properties held.
 
